### 2017-07-19 Work_report/Daily_progress/work_progress_daily.tex
Starting the btp project

\documentclass{article}
\usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
\usepackage{hyperref}
% \usepackage{titlesec}

\newcommand{\ra}{$\rightarrow$}

\title{Btech Project - Progress Diary}
\author{
  Arka Sadhu}
\date{\today}

\begin{document}
\maketitle

\tableofcontents
\newpage
\section{Daily Progress}

\end{document}

### 2017-07-20 Work_report/Daily_progress/work_progress_daily.tex
Adding papers, and progress report with paper abstracts

@@
 \usepackage{hyperref}
-% \usepackage{titlesec}
+\usepackage{float}
+\usepackage{caption}
+\usepackage{subcaption}
+% \usepackage{siunitx}
+% \sisetup{round-mode=places,round-precision=2}
 
@@
 \section{Daily Progress}
+\subsection{Week 1 : July 17 - July 23}
+\subsubsection{July 17 : Monday}
+Accomplished :
+\begin{itemize}
+\item Met prof and discussed basic project about deep learning and image co-segmentation.
+\item Prof asked to mail and contact sayan banerjee.
+\end{itemize}
+
+\subsubsection{July 18 : Tuesday}
+Accomplished :
+\begin{itemize}
+\item Mailed Sayan banerjee, but seems like he has a fever, and also didn't give/suggest any papers unfortunately.
+\item Only saw one image cosegmentation paper by Inria, but didn't have the time to read it.
+\end{itemize}
+
+\subsubsection{July 19 : Wednesday}
+Accomplished :
+\begin{itemize}
+\item Dowloaded a few papers to read.
+\item Init git repository and added basic work report format (from viterbi internship project).
+\end{itemize}
+
+\subsubsection{July 20 : Thursday}
+Target :
+\begin{itemize}
+\item Try to meet up with Prof/ Sayan and discuss about possible extensions.
+\item Brainstorm ideas as and when time permits.
+\item Read as many papers as possible. Complete in-depth reading is not required, simple reading of abstract and reading the relevant papers should be enough.
+\end{itemize}
+
+Accomplished :
+\begin{itemize}
+\item Read the 3 papers :
+  \begin{itemize}
+  \item Discriminative clustering for image co-segmentation \cite{5539868}: abstract gives basic definition of image co-segmentation as well as says unsupervised segmentation of image into foreground and background regions is still a challenging task.
+Should be worth reading.
+Images are also as requried.
+  \item Automatic Image Co-segmentation using geometric saliency \cite{7025663}: says co-labelling of multiple images is a complex process, instead suggests segmentation on individual images but based on a saliency map obtained by fusing saliency maps of groups of similar images.
+Images are also as required.
+Since it is anyways small, should be worth reading.
+  \item Unsupervised 3D shape segementation and co-segmentation via deep learning \cite{SHU201639}: should have been the most related but turns out they do something quite different (at least from first look).
+They try to automatically segment a single 3D shape or co-segment family of 3D shape.
+For this they use pre-decompose 3D shape into primitive patches to compute various low level features, then learn high level features in an unsupervised style from low level features based on deep learning, and finally either segmentation or co-segmentation results are fot by patch clustering in high level feature space.
+The input images are 3D and not 2D as originally required, as such the paper is on Comptuer graphics apparently.
+But it should be interesting to read the deep learning part of it, i.e.
+how did they learn the high level features in the unsupervised style from low level features.
+  \end{itemize}
+\end{itemize}
+
+\bibliography{./papers.bib}
+\bibliographystyle{ieeetr}
+% \nocite{*}
 

### 2017-07-26 Work_report/Daily_progress/work_progress_daily.tex
Adding a few papers
Adding paper review #1

@@
 
+\subsubsection{July 21 : Friday}
+No work done.
+
+\subsubsection{July 22 : Saturday}
+No work done
+
+\subsubsection{July 23 : Sunday}
+No work done.
+
+\subsubsection{July 24 : Monday}
+Meeting with Sayan. Discussion about some basic problems that could be solved. Apparently Video Co-segmentation using Deep learning is not yet looked upon. May be a good breakthrough.
+
+\subsubsection{July 25 : Tuesday}
+Target :
+\begin{itemize}
+\item Read the three papers. \cite{7120111} , \cite{7401081}, \cite{Zhang2014}
+\end{itemize}
+
+Accomplished :
+\begin{itemize}
+\item Able to read only 1 paper properly (not too properly).
+\end{itemize}
+
+\subsubsection{July 26 : Wednesday}
+
+\begin{itemize}
+\item Couldn't do much. Need to do paper review at the very first.
+\item Need to do pytorch tutorials as well.
+\item Paper review to be done in a separate file.
+\end{itemize}
+
 \bibliography{./papers.bib}
 \bibliographystyle{ieeetr}
-% \nocite{*}
+
+%\nocite{*}
 

### 2017-07-26 Work_report/Paper Reviews/Paper_reviews.tex
Adding paper review #1

\documentclass{article}
\usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
% \usepackage{siunitx}
% \sisetup{round-mode=places,round-precision=2}

\newcommand{\ra}{$\rightarrow$}

\title{Paper Reviews}
\author{
  Arka Sadhu}
\date{\today}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Unsupervised Co-segmentation for Indefinite Number of Common Foreground Objects}
\cite{7401081}
\subsection{Abstract}
\begin{itemize}
\item Co-segmentation addresses the problem of simultaneously extracting the common targets appeared in Multiple images.
\item Keywords : Co-segmentation, multi-object discovery, adaptive feature, loopy belief propagation
\end{itemize}

\subsection{Introduction}
The paper extends the previous proposal Selection based Co-segmentation[PSCS] methods with the 3 major contributions :
\begin{itemize}
\item Key problem in [PSCS] is mining consistent information shared by the common targets. May require manual selection of features, or feature learning performed beforehand. Here : (simple and effective) self-adaptive feature selection strategy is introduced.
\item Many assume each image contains a single common target and fail for multiple common targets images to extract all targets. Here proposal selection based Unsupervised Co-segmentation [PSUCS] is introduced.
\item For multiple common targets, multi-class co-segmentation approaches do not do so well because of significant appearance variance and the inconsistent number of common targets, also some combinational common trgets are usually splitted into multiple pieces. Here : an adaptive strategy that can handle Indefinite number of common targets involved cases, where each image may contain different number of common targets.
\end{itemize}

\subsection{Problem Formulation}
\begin{itemize}
\item Image set $I = {I_i}, i = {1...M}$, images may contain different number of targets, goal is to extract all common targets.
\item Given $I_i$ generate proposal set $P_i = {p_i^k}, k = {1...K_i}$, set large value for $K$, to make sure that the object proposal set covers all potential common targets.
\item Cos for indefinite number of common targets is transformed into a labeling problem, given $p_i^k$, $x_i^k = 1$ for foreground, else $0$.
\item Union set is viewed as final segmentation result $$R_i = \bigcup \{p_i^k | x_i^k, k \le K_i\}$$
\item Here, the labeling problem in a completely connected network., where each object proposal [OP] is a node, and connected with weighted edges.
\item \underline{Multiple OP of each image is conducted separately}, but closely related to other images of the collection.
\item For each image $I_i$, choose a proposal in every selecting loop to be the real foreground, and in choosing the new loop, we remove the node of the previous proposal to make sure this new proposal would be considered a target, whether this will be chosen as a target depends totally on the labels of other images.
\item \textbf{Therefore}, segmentation problem of image of $I_i$ finally becomes finding an optimal labeling set $x_i = \{x_i^k|k = 1...K_i; x_k \in \{0,1\}\}$ by max the energy function (refer to the paper) : function of weights of the edges and some other constraints.
\item Weight is non-zero and numerically equal to a similarity score between the proposals (to be introduced later). The constraints mean, for each image only one proposal could be selected per loop, and every proposal in image $I_i$ can be selected only once throughout the selection procedure.
\item The formulation is based on the fact that common targets have same characters, and maximizing overall similarity with additional constraint we can make sure newly chosen object proposal is the most similar one to the chosen proposal of the other image. This can be solved via greedy optimization.
\end{itemize}

\subsection{Co-segmentation for Indefinite Number of Common Targets}
Key is to adaptively determining the number of targets, which require fully extracting teh potential targets and then mining the conistent relationships shared by teh common targets.

\subsubsection{Overall Framework}
\begin{enumerate}
\item Category independent OP generated.
\item Connected graph with all proposals as nodes and edge weights as proposal similarities.
\item For reliable similarity, adaptive feature weight selection algorithm.
\item Multiple common targets [MCT] searching, where [MCT] are extracted for each individual image.
\item Terminal condition designed as the common target judging criterion.
\item After termination, simply collect selected proposals.
\end{enumerate}

\subsubsection{Object Proposals Generation}
\begin{enumerate}
\item Very important, directly impacts the performance of Co-segmentation.
\item Measurement of the proposal pool contains mainly two aspects :
  \begin{itemize}
  \item Diversity : cover as many objects as possible.
  \item Representativeness : as few candidates as possible for each object.
  \end{itemize}
\item After a large number of proposals are achieved, a scoring mechanism that combines appearance features and overlap penalty is raised for proposal ranking. There is problem of the proposal containing a local part, but the proposed method could make up for such loss by conducting multiple targets searching.
\end{enumerate}

\subsubsection{Weighted Graph Construction}
\begin{itemize}
\item Usual way : measuring similarity between every two proposals.
\item Choosing fixed features for similarity is not a good option. Adopting a flexible and reliable proposal similarity measurement. Here : Unsupervised self-adaptive similarity measurement is introduced for calculating edge weights. Highly efficient and easy to implement. Example in two images colors might be same, in two other images color might be drastically different.
\item Use iterative weights setting mechanism for the features. Initial proposal labels using loopy belief algo previously, and then iterating to maximize a function.
\item The intuitive intention : encourage selected common targets to be globally consistent while keping a low variance to make the similarity metric more reasonable and representative.
\end{itemize}

\subsubsection{Common Targets Multi-Search Strategy}
Adaptive common target searching strategy that can deal with any numbers of targets.

\begin{itemize}
\item For more common targets , remove previously discovered ones from the candidate pool.
\item Initialize labels $x^{*}$ from prev algo. Basically selecting most likely common targets, by removing the prev most likely common target.
\item Get an adaptive threshold.
\end{itemize}

\section{Video Object Co-segmentation by Regulated Maximum Weight Cliques}
\cite{Zhang2014}
\section{Object-Based Multiple Foreground Video Co-Segmentation via Multi-State Selection Graph}
\cite{7120111}

\bibliography{../Daily_progress/papers.bib}
\bibliographystyle{ieeetr}

%\nocite{*}

\end{document}

### 2017-07-26 Work_report/Paper Reviews/Paper_reviews.tex
Adding paper #2

@@
 \cite{Zhang2014}
+
+\subsection{Abstract}
+\begin{itemize}
+\item Novel approach for object co-segmentation in arbitrary videos by sampling, tracking, and matching [OP] via a Regulated Maximum Weight Clique [RMWC] extraction scheme.
+\item Achieves good results by pruning away noisy segments in video through selection of [OP] tracklets athat are spatially salient and temporally consistent, and by iteratively extracting weighted groupings of objects with similar shape and appearance (with-in and across videos).
+\item Approach is general and handles : multiple objects, temporary occlusions, objects going in and out of view, also doesn't make any prior assumption on the commonality of the objects in the video collection.
+\item Keywords : Video Segmentation, Co-segmentation
+\end{itemize}
+
+\subsection{Introduction and Related Work}
+Goal is to discover and segment objects from a video collection in an unsupervised manner.
+
+\begin{itemize}
+\item Video Co-segmentation is natural extension of Image Co-segmentation.
+\item In general for video cos, appearance info to group pixels in a spatio-temporal grpah and/or employ motion segmentation techniques to separate objects by using motion cues.
+\item Previous work use strong assumptions of single class of object common to all videos.
+\item The work has the following advantages :
+  \begin{itemize}
+  \item Employs object tracklets as opposed to pixel-level or region-level to perform clustering.
+The eprceptual grouping of pixels before matching reduces segement fragmentation and leads to a simpler matching problem.
+  \item No approximate solution. [RMWC] has an optimal solution. Using only object tracklets keeps the computation cost low.
+  \item Can handle occlusions, or objects going in and out of the video because the object tracklets are temporally local and there is no requirements for the object to continuously remain in the field of view of the video.
+Also no limit on teh number of object classes in the each video and number of common object clases in teh video collection.
+Therefore more general.
+  \item Different from [MWC], in that it is regulated by intra-clique consistency term, as a result produces more global consistency.
+  \end{itemize}
+\end{itemize}
+
+\subsection{Regulated Maximum Weight Clique based Video Co-segmentation}
+\subsubsection{Framework}
+Two stages :
+\begin{enumerate}
+\item Object Tracklet Generation : generate [OP] for each frame and use each of them as a starting point and track the object proposals backward and forward trhoughout the whole video seq, and generate reliable tracklets from the track set and perform non-maxima suppression to remove noisy or overlapping proposals.
+\item Multiple Objects Co-segmentation by Regulated Maximum Weight Cliques : Tracklets as node, and the nodes are weighted by tracklet similarity, and edges with weight below a threshold are removed.
+[RMWC] to find objects ranked by score which is a combination of intra-group consistency and Video Object scores.
+\end{enumerate}
+
+\subsubsection{Object Tracklets Generation}
+\begin{itemize}
+\item Generate a number of [OP]. Each proposal has a Video Object Score : combination of motion and appearance. $$S^{object}(x) = A(x) + M(x)$$
+\item $A(x)$ : appearance score described directly by algo. High for regions with closed boundary in space, different appearance from its surroundings and is salient.
+\item $M(x)$ : motion score defined as the average frob norm of optical flow gradient around the boundary of object proposal.
+\item Efficient Object Proposal Tracking :
+  \begin{itemize}
+  \item Track every object proposal from each frame backward and forwar to form a number of tracks for the object.
+  \item Combined color (color histograms to model appearance)+ location(overlap ratio) + shape similarity (contour of region in normalized polar coordinates and sampling it from 0 - 360 deg to form a vector) and then dot product for the first and last.
+  \item Greedy tracking : most similar object proposal is selected to be tracked down, computationally requires fnding index of max value in a specific row of the similarity matrix and hence economical.
+  \end{itemize}
+\item Non-maximum Suppression [NMS] for Object Proposal Tracks :
+  \begin{itemize}
+  \item Need to prune duplicate (near-duplicate) tracks.
+  \item Video Object score for one track is obtained, and see $R_{overlap} > 0.5$ and remove them.
+  \item After [NMS] small percentage of total tracks are retained, and to ensure validity of the track associations, remove associations that are 1.5 std from the mean track similarity.
+  \end{itemize}
+\end{itemize}
+
+\subsubsection{Multiple Object Co-segmentation by [RMWC]}
+After object tracklets are obtained, need salient object groupings in the video collection. Grouping problem is formulated as Regulated Maximum Weight Clique.
+
+\begin{itemize}
+\item Clique Problems :
+  \begin{itemize}
+  \item Given G = (V,E,W), a clique is complete subgraph of G, i.e. one whose vertices are pairwise adjacent.
+  \item Maximal Clique is a complete subgraph not contained in any other complete subgraph.
+  \item Finding all maximal Clique is NP-hard. Maximum Clique problem is to find the  Maximum complete subgraph and Maximum Weight Clique problem deals with finding the Clique with max weight.
+  \end{itemize}
+\item Problem Constraints :
+  \begin{itemize}
+  \item Object Proposal Tracklets [OPT] : similar appearance both in video and across video, for in-video L channel used, for across a,b also used.
+  \item Shape of same object would not change in the same video, and hence used for building tracklets of same objects in a video.
+  \item Dominant object =$>$ high Video Object Score [VOS]
+  \item Tracklets generated by an object should have low variation.
+  \end{itemize}
+\item Graph Structure :
+  \begin{itemize}
+  \item Object tracklets [OT] are nodes, inter and intra video edges created as described above.
+  \item Weak edges removed by a threshold.
+  \end{itemize}
+\item RMWC :
+  \begin{itemize}
+  \item Get weight of node.
+  \item According to formulation : Clique that has the highest score represents the object with largest combined score of inter-object consistency and objectness.
+Use NP hard formulation, but doesn't hinder its usage, as number of tracklets are limited, and takes less than a second on standard laptop.
+  \end{itemize}
+\end{itemize}
+
 \section{Object-Based Multiple Foreground Video Co-Segmentation via Multi-State Selection Graph}

### 2017-07-27 Work_report/Paper Reviews/Paper_reviews.tex
Adding paper #3

@@
 \usepackage{subcaption}
+\usepackage{amssymb}
+
 % \usepackage{siunitx}
@@
 
-\title{Paper Reviews}
+\title{Paper Summaries}
 \author{
@@
 \cite{7120111}
+\subsection{Abstract}
+\begin{itemize}
+\item Multiple foreground Video Co-segmentation for a set of videos.
+\item Foreground object in each frame considering intra-video coherence of the fg as well as fg consistency among teh different videos in the set.
+\item Multiple foreground handled by multi-state selection graph, node is a video frame, can take multiple labels that correspond to different objects.
+Also indicator matrix to handle incorrect classification of irrelevant regions.
+\item Iterative algo to optimize the function.
+\item Index terms : Video Co-segmentation, Multiple Foregrounds, object-based Segmentation
+\end{itemize}
+
+\subsection{Introduction}
+\begin{itemize}
+\item Video foreground Co-segmentation aims at jointly extracting the main common objects present in a given set of videos.
+\item Low level may not accurately discriminate fg and bg. Also object based method for single video do not exploit joint info between the videos. Here : handle Multiple fg object in Multiple videos.
+\item OP as basic pre-processing. Mid-level features result in more robus and meaningful separation of fg and bg.
+\item Graph : nodes is video frames, state : to indicate which object proposal is chosen.
+\item Edges between adjacent frames in a video so as to enforce spatio-temporal smoothness of the trajectory of the fg object, while edges beetween frames of different videos are added to emasure foreground consistency.
+\item Multi state selection graph [MSG] for multiple states of the nodes to handle multiple Foregrounds.
+The basic subgraph is replicated multiple times with each replicated subgraph representing a particular foreground object.
+Can be optimized using existing methods.
+\item Relax the condition of existence of the common foreground in all the videos, the method will segment unrelated regions in place of the missing object, and use and indicator matrix to correctly deal with the missing common objects.
+\end{itemize}
+
+\subsection{Multi-state selection Graph}
+\begin{itemize}
+\item Object in a video is a fg if :
+  \begin{itemize}
+  \item High appearance contrast relative to the bg.
+  \item Trajectory of fg object across consecutive video frames is smooth, appearnace and shape are also similar across frames.
+  \item In a video fg object appers in each frame.
+  \item Additional constraint : on common fg object that they maintain a consistent appearance across different videos.
+  \end{itemize}
+\item Basic subgraph G = (V, E).
+Define energy function, $\psi$ for nodes, $\phi$ for edges, and $u_n$ a state taken by each node n in a discrete space.
+Configuration of states can be done by minimizing the energy function.
+We seek multiple solutions that are as independent as possible.
+Introduce a diversity term and define a new optimization problem for MSG.
+\item Replicate the basic subgraph K-1 times, to get a total of K, diversity term is incorporated as the edges between teh corresponding nodes in the basic subgraphs, and combined into a unified graph to get a new energy function and it shares the same formulation as the standard graph, so it can be solved directly by existing energy minimization methods to yiedl all of the multiple states at once.
+\end{itemize}
+
+\subsection{Object Based Video Co-segmentation}
+Suppose V videos, and each video consists of $T_v$ frames. In the MSG, intra-video edges placed between the nodes of adjacent frames, and inter-video edges are fully connected.
+
+\subsubsection{MSG for Video Co-segmentation}
+\begin{itemize}
+\item MSG selects same number of states for each node, i.e.
+the object must appear in each frame of each video.
+Assumption doesn't hold in general.
+Use indicator matrix $Y \in \mathbb{R}^{V \times K}$, with $y_{vk} = 1$ to denote video v contains object k.
+\item Get a new energy function with $y_{vk}$.
+\end{itemize}
+
+\subsubsection{Term Definitions}
+\begin{itemize}
+\item Unary Term :
+  \begin{itemize}
+  \item $\Psi(.)$ combines three factors (objectness score, motion score, saliency score) for determining the likelihood that an object candidate is the Foreground.
+Saliency score is considered since the object may not always be moving.
+Co-saliency is different from saliency : discovers common saliency among multiple images.
+  \item Here : compute co-saliency map for each frme and then calculate the mean co-saliency value for each candidate region as the saliency score $S(u)$.
+  \end{itemize}
+\item Intra Video Term :
+  \begin{itemize}
+  \item $\Phi_a(., .)$ provides a spatio temporal smoothness constraint between neighboring frames in an individual video.
+  \item Uses estimated based on iou with wrapped region w.r.t optical flow mapping.
+  \end{itemize}
+\item Inter-video Term :
+  \begin{itemize}
+  \item $\Phi_b(.,.)$ measures Foreground consistency among the videos, considering $\chi^2$ color distances of color histograms and HOG descirptors.
+  \end{itemize}
+\item Diversity Term :
+  \begin{itemize}
+  \item $\Delta(.,.)$ to avoid selecting teh same object in different candidate series. Again IOU.
+  \end{itemize}
+\end{itemize}
+
+\subsubsection{Optimization Procedure}
+\begin{itemize}
+\item In special cases with fixed indicator matrices $\textbf{Y}$, can be solved directly using existing formulations.
+\item If not fixed, develop iterative procedure to approximately update two sets of variables (Y, U) until convergence.
+\item Multiple Foreground video Co-segmentation method :
+  \begin{itemize}
+  \item Initialize Y to all 1
+  \item Solve for u.
+  \item Update Y.
+Irrelevant regions have relatively lower unary scores than actual foregrounds.
+Once $y_{vk}$ updated to 0, can never become 1, to avoid this instead of setting it to 0, set it to $\epsilon (0.0001)$.
+  \item Termination : if Y doesn't chage or upon reaching max number of iterations.
+  \item Pixel-level Post process : Refine teh selected objects through a pixel-level post-process by usuing a spatiotemporal graph based segmentation method.
+  \end{itemize}
+\end{itemize}
 

### 2017-07-27 Work_report/Paper Reviews/Paper_reviews.tex
Fixed minor spell errors

@@
 Here proposal selection based Unsupervised Co-segmentation [PSUCS] is introduced.
-\item For multiple common targets, multi-class co-segmentation approaches do not do so well because of significant appearance variance and the inconsistent number of common targets, also some combinational common trgets are usually splitted into multiple pieces.
+\item For multiple common targets, multi-class co-segmentation approaches do not do so well because of significant appearance variance and the inconsistent number of common targets, also some combinational common targets are usually split into multiple pieces.
 Here : an adaptive strategy that can handle Indefinite number of common targets involved cases, where each image may contain different number of common targets.
@@
 \subsection{Co-segmentation for Indefinite Number of Common Targets}
-Key is to adaptively determining the number of targets, which require fully extracting teh potential targets and then mining the conistent relationships shared by teh common targets.
+Key is to adaptively determining the number of targets, which require fully extracting the potential targets and then mining the consistent relationships shared by the common targets.
 
@@
 \item Use iterative weights setting mechanism for the features. Initial proposal labels using loopy belief algo previously, and then iterating to maximize a function.
-\item The intuitive intention : encourage selected common targets to be globally consistent while keping a low variance to make the similarity metric more reasonable and representative.
+\item The intuitive intention : encourage selected common targets to be globally consistent while keeping a low variance to make the similarity metric more reasonable and representative.
 \end{itemize}
@@
 \item Novel approach for object co-segmentation in arbitrary videos by sampling, tracking, and matching [OP] via a Regulated Maximum Weight Clique [RMWC] extraction scheme.
-\item Achieves good results by pruning away noisy segments in video through selection of [OP] tracklets athat are spatially salient and temporally consistent, and by iteratively extracting weighted groupings of objects with similar shape and appearance (with-in and across videos).
+\item Achieves good results by pruning away noisy segments in video through selection of [OP] tracklets that are spatially salient and temporally consistent, and by iteratively extracting weighted groupings of objects with similar shape and appearance (with-in and across videos).
 \item Approach is general and handles : multiple objects, temporary occlusions, objects going in and out of view, also doesn't make any prior assumption on the commonality of the objects in the video collection.
@@
 \item Video Co-segmentation is natural extension of Image Co-segmentation.
-\item In general for video cos, appearance info to group pixels in a spatio-temporal grpah and/or employ motion segmentation techniques to separate objects by using motion cues.
+\item In general for video cos, appearance info to group pixels in a spatio-temporal graph and/or employ motion segmentation techniques to separate objects by using motion cues.
 \item Previous work use strong assumptions of single class of object common to all videos.
@@
   \item Employs object tracklets as opposed to pixel-level or region-level to perform clustering.
-The eprceptual grouping of pixels before matching reduces segement fragmentation and leads to a simpler matching problem.
+The perceptual grouping of pixels before matching reduces segment fragmentation and leads to a simpler matching problem.
   \item No approximate solution. [RMWC] has an optimal solution. Using only object tracklets keeps the computation cost low.
   \item Can handle occlusions, or objects going in and out of the video because the object tracklets are temporally local and there is no requirements for the object to continuously remain in the field of view of the video.
-Also no limit on teh number of object classes in the each video and number of common object clases in teh video collection.
+Also no limit on the number of object classes in the each video and number of common object classes in the video collection.
 Therefore more general.
@@
 \begin{enumerate}
-\item Object Tracklet Generation : generate [OP] for each frame and use each of them as a starting point and track the object proposals backward and forward trhoughout the whole video seq, and generate reliable tracklets from the track set and perform non-maxima suppression to remove noisy or overlapping proposals.
+\item Object Tracklet Generation : generate [OP] for each frame and use each of them as a starting point and track the object proposals backward and forward throughout the whole video seq, and generate reliable tracklets from the track set and perform non-maxima suppression to remove noisy or overlapping proposals.
 \item Multiple Objects Co-segmentation by Regulated Maximum Weight Cliques : Tracklets as node, and the nodes are weighted by tracklet similarity, and edges with weight below a threshold are removed.
@@
   \begin{itemize}
-  \item Track every object proposal from each frame backward and forwar to form a number of tracks for the object.
+  \item Track every object proposal from each frame backward and forward to form a number of tracks for the object.
   \item Combined color (color histograms to model appearance)+ location(overlap ratio) + shape similarity (contour of region in normalized polar coordinates and sampling it from 0 - 360 deg to form a vector) and then dot product for the first and last.
-  \item Greedy tracking : most similar object proposal is selected to be tracked down, computationally requires fnding index of max value in a specific row of the similarity matrix and hence economical.
+  \item Greedy tracking : most similar object proposal is selected to be tracked down, computationally requires finding index of max value in a specific row of the similarity matrix and hence economical.
   \end{itemize}
@@
 \item Multiple foreground Video Co-segmentation for a set of videos.
-\item Foreground object in each frame considering intra-video coherence of the fg as well as fg consistency among teh different videos in the set.
+\item Foreground object in each frame considering intra-video coherence of the fg as well as fg consistency among the different videos in the set.
 \item Multiple foreground handled by multi-state selection graph, node is a video frame, can take multiple labels that correspond to different objects.
@@
 \item Low level may not accurately discriminate fg and bg. Also object based method for single video do not exploit joint info between the videos. Here : handle Multiple fg object in Multiple videos.
-\item OP as basic pre-processing. Mid-level features result in more robus and meaningful separation of fg and bg.
+\item OP as basic pre-processing. Mid-level features result in more robust and meaningful separation of fg and bg.
 \item Graph : nodes is video frames, state : to indicate which object proposal is chosen.
-\item Edges between adjacent frames in a video so as to enforce spatio-temporal smoothness of the trajectory of the fg object, while edges beetween frames of different videos are added to emasure foreground consistency.
+\item Edges between adjacent frames in a video so as to enforce spatio-temporal smoothness of the trajectory of the fg object, while edges between frames of different videos are added to measure foreground consistency.
 \item Multi state selection graph [MSG] for multiple states of the nodes to handle multiple Foregrounds.
@@
   \item High appearance contrast relative to the bg.
-  \item Trajectory of fg object across consecutive video frames is smooth, appearnace and shape are also similar across frames.
-  \item In a video fg object appers in each frame.
+  \item Trajectory of fg object across consecutive video frames is smooth, appearance and shape are also similar across frames.
+  \item In a video fg object appears in each frame.
   \item Additional constraint : on common fg object that they maintain a consistent appearance across different videos.
@@
 Introduce a diversity term and define a new optimization problem for MSG.
-\item Replicate the basic subgraph K-1 times, to get a total of K, diversity term is incorporated as the edges between teh corresponding nodes in the basic subgraphs, and combined into a unified graph to get a new energy function and it shares the same formulation as the standard graph, so it can be solved directly by existing energy minimization methods to yiedl all of the multiple states at once.
+\item Replicate the basic subgraph K-1 times, to get a total of K, diversity term is incorporated as the edges between the corresponding nodes in the basic subgraphs, and combined into a unified graph to get a new energy function and it shares the same formulation as the standard graph, so it can be solved directly by existing energy minimization methods to yield all of the multiple states at once.
 \end{itemize}
@@
 Co-saliency is different from saliency : discovers common saliency among multiple images.
-  \item Here : compute co-saliency map for each frme and then calculate the mean co-saliency value for each candidate region as the saliency score $S(u)$.
+  \item Here : compute co-saliency map for each frame and then calculate the mean co-saliency value for each candidate region as the saliency score $S(u)$.
   \end{itemize}
@@
   \begin{itemize}
-  \item $\Phi_b(.,.)$ measures Foreground consistency among the videos, considering $\chi^2$ color distances of color histograms and HOG descirptors.
+  \item $\Phi_b(.,.)$ measures Foreground consistency among the videos, considering $\chi^2$ color distances of color histograms and HOG descriptors.
   \end{itemize}
@@
   \begin{itemize}
-  \item $\Delta(.,.)$ to avoid selecting teh same object in different candidate series. Again IOU.
+  \item $\Delta(.,.)$ to avoid selecting the same object in different candidate series. Again IOU.
   \end{itemize}
@@
 Once $y_{vk}$ updated to 0, can never become 1, to avoid this instead of setting it to 0, set it to $\epsilon (0.0001)$.
-  \item Termination : if Y doesn't chage or upon reaching max number of iterations.
-  \item Pixel-level Post process : Refine teh selected objects through a pixel-level post-process by usuing a spatiotemporal graph based segmentation method.
+  \item Termination : if Y doesn't change or upon reaching max number of iterations.
+  \item Pixel-level Post process : Refine the selected objects through a pixel-level post-process by using a spatiotemporal graph based segmentation method.
   \end{itemize}

### 2017-07-29 Work_report/Daily_progress/work_progress_daily.tex
Updating daily work progress with bib file

@@
 
+\subsubsection{July 27 : Thursday}
+Accomplished :
+\begin{itemize}
+\item Completed reading all the papers and joting down main points of the paper.
+\item Meeting with Sayan (main points written below):
+  \begin{itemize}
+  \item Video Co-segmentation hasn't been worked on by the Vision community yet.
+  \item The main aim is to make an end-to-end model using RNN.
+  \item To circumvent problems of vanishing gradients, we can use LSTM. But for our problem, even LSTM might not suffice.
+  \item Hence we can use Memory Augmented LSTM, which should be able to take care of the vanishing gradients.
+  \item There is no big datasets for the purpose of Video Co-segmentation. Hence we can look at Weakly unsupervised learning techniques to circumvent this problem.
+  \item Need to read 5 papers at the earliest (by Monday).
+\cite{DBLP:journals/corr/SiamVJR16}, \cite{DBLP:journals/corr/JainZSS15}, \cite{PAVEL2017105}, \cite{DBLP:journals/corr/NohHH15}, \cite{DBLP:journals/corr/GulcehreCB17}
+  \end{itemize}
+\end{itemize}
+
+\subsubsection{July 28 : Friday}
+No work done
+
+\subsubsection{July 29 : Saturday}
+
 \bibliography{./papers.bib}

### 2017-07-29 Work_report/Paper Reviews/Paper_reviews.tex
Adding paper #4
But I feel I haven't been able to understand the paper in its entirety

@@
 
+\section{Convolutional Gated Recurrent Networks for Video Segmentation}
+\cite{DBLP:journals/corr/SiamVJR16}
+\subsection{Abstract}
+\begin{itemize}
+\item Novel approach to implicitly utilize temporal data in videos for online Segmentation. Relies on FCN embedded into a gated recurrent architecture.
+\item The design receives a sequence of consecutive video frames and outputs the segmentation of the last frame.
+\item Convolutional gated Recurrent networks are used for the recurrent part to preserve spatial connectivities in the image.
+\item Works on both online and batch segmentation. Tested for both binary and semantic segmentation part.
+\end{itemize}
+
+\subsection{Introduction}
+\begin{itemize}
+\item \textbf{Video segmentation} extensively investigated using classical approaches.
+Mainly focuses on semi-supervised approaches that propagate the labels in one or more annotated frames to the entire video.
+\item \textbf{Gated Recurrent Architectures} alleviate problem of vanishing or exploding gradients in RNN.
+LSTM is one of the earliest attempts to design it.
+Gated Recurrent Unit [GRU] is a more recent attempt, having similar performance to LSTM with reduced number of gates thus fewer parameters.
+\item Problem : They accept only vectors and hence do not preserve spatio-temporal information.
+Convolutional GRU can circumvent the problem and has been used for video captioning and action recognition.
+\item Here : Gated Recurrent FCN. Contributions :
+  \begin{itemize}
+  \item Incorporate temporal data to FCN for video Segmentation. Convolutional Gated Recurrent FCN to efficiently utilze spatiotemporal information.
+  \item End-to-end model for video segmentation.
+  \item Experimental analysis on binary segmentation and video semantic segmentation.
+  \end{itemize}
+\end{itemize}
+
+\subsection{Background}
+Review of FCN and RNN.
+\subsubsection{Fully Convolutional Networks (FCN)}
+\begin{itemize}
+\item All fully connected layers are replaced with convolution layers.
+Allows input of any size, since it is not restricted to a fixed output size, fully connected layers.
+Can get a coarse segmentation output (heat map) by only one forward pass of the network.
+\item Need to upsample the coarse map, and instead of simple bi-linear interpolation, adaptive up-sampling is shown to have better result.
+Can have learnable layers to learn the up-sampling weights through back-propagation.
+These are called deconvolution layers.
+\item Skip architecture can be used for finer Segmentation. Here, heat maps from earlier architecture are merged with the final heat map for an improved  Segmentation.
+\end{itemize}
+
+\subsubsection{Recurrent Neural Networks}
+\begin{itemize}
+\item RNN can be applied on a sequence of inputs and are able to capture the temporal relation betwen them.
+\item Hidden unit in each recurrent cell allows it to have dynamic memory that is changing according to what it had before.
+\item For longer vectors it causes vanishing gradients. ated recurrent architectures have been proposed as a solution and empiricially useful for many tasks.
+\item \textbf{Long Short Term Memory (LSTM)}
+  % \begin{itemize}
+  % \item
+    LSTM utilizes three gates to control flow of signal : input, output, forget gate, each with own set of weights and learned with back-propagation.
+At the inference stage, values in the hidden unit ican be roughly interpreted as a memory, and used for prediciton of the current state.
+  % \end{itemize}
+\item \textbf{Gated Recurrent Unit (GRU)}
+  % \begin{itemize}
+  % \item
+    Same principal as LSTM, with simpler architecture, less computationally expensive, and requires less memory.
+  % \end{itemize}
+\end{itemize}
+
+\subsection{Method}
+A Recurrent Fully Convolutional Network (RFCN) is designed that utilizes tge spatio-temporal information. Two approaches are explored : conventional recurrent units, convolutional recurrent units.
+
+\subsubsection{Conventional Recurrent Architecture for Segmentation}
+\begin{itemize}
+\item \textbf{RFC-LeNet}
+  \begin{itemize}               %
+  \item Fully convolutional version of LeNet which is a shallow network, used for baseline comparisons.
+  \item Output of deconvolution fo 2D map of dense predicitons is flattened into 1D vector as the input to a conventional Recurrent unit, and the unit takes this vector for each frame in teh sliding window and outputs the Segmentation of the last frame.
+  \end{itemize}
+\item \textbf{RFC-12s}
+  \begin{itemize}
+  \item Apply the recurrent layer on the down-sampled heatmap before deconvolution.
+  \item The recurrent unit operates on coars maps to produce a coarse map corresponding to the last frame in the sequence.
+  \end{itemize}
+\end{itemize}
+
+\subsubsection{Convolutional Gated Recurrent Architecture (Conv-GRU) for Segmentation}
+\begin{itemize}
+\item Conventinal recurrent units are designed for text processing and not image processing, and directly using for images has pains :
+  \begin{itemize}
+  \item The size of weight parameters becomes very large since vectorized images are large
+  \item Spatial connectivity between pixels are ignored.
+  \end{itemize}
+\item Convolutional Recurrent units, convolve 3D weights with their input.
+Dot products replaced by convolutions.
+Learning filters that convolve with the entire imagee instead of individual weights for pixels, makes it much more efficient.
+\item \textbf{RFC-VGG}
+  % \begin{itemize}
+  % \item
+    Intermediate faeture maps are fed into a convlutional atead recurrent unit, and then a convolutional layer converts its output to a heat map.
+  % \end{itemize}
+\item \textbf{RFCN-8s} : Recurrent verison of FCN-8s architecture.
+\end{itemize}
+
 \bibliography{../Daily_progress/papers.bib}

### 2017-08-01 Work_report/Paper Reviews/Paper_reviews.tex
Adding paper #5

@@
 
+\section{Structural RNN : Deep Learning on Spatio-temporal Graphs}
+\cite{DBLP:journals/corr/JainZSS15}
+\subsection{Abstract}
+\begin{itemize}
+\item Deep RNN capable at modelig seqeunces, lack an intuitive highlevel spatio-temporal sturcutre which are popular tool for imposting such highlevel intuitions in the formulations of real world problems.
+\item Develop a scalable method for casting an arbitratry spatio-temporal graph as a rich RNN mixture that is feedforward fully differentialble, and jointly trainable.
+\item Shows imporvement over sotawith a large margin.
+\end{itemize}
+
+\subsection{Introduction}
+\begin{itemize}
+\item Spatio-temporal [st] graphs are popular tool for representing such high-level spatio-temporal structures.
+The nodes represent the Problem components, and the edges capture their spatio-temporal interactions.
+\item Here [st] graph into sturctural RNN [S-RNN].
+\item In high-level steps, given any arbitrary st-graph :
+  \begin{itemize}
+  \item Roll it out in time and decompose it into a set of contributing factor components.
+  \item The factors identify the independent components that collectively determine one decision and are derived from both edges and nodes fo the st-graph.
+  \item Semantically group thefactor componeonts and represent each group using one RNN which results in the desired RNN mixture.
+  \item Main challenges of the transformation is :
+    \begin{itemize}
+    \item Making the RNN mixture as rich as possible to enable learning complex functions : represent  each st factor using one RNN.
+    \item Keeping the RNN mixture scalable with respect to size of the input st-graph : factor sharing between RNNs.
+    \end{itemize}
+  \end{itemize}
+\item Proposed method is generic and applicable to any problem formulated using st-graph. Enjoys underlying high-level structure.
+\end{itemize}
+\subsection{SRNN architecture}
+\subsubsection{Representation of spatio-temporal Graphs}
+\begin{itemize}
+\item St-graph : $G = (V, E_s, E_T)$ whose structure $(V,E_s)$ rolls over time through edges $E_T$.
+\item The nodes $v \in V$ and $e \in E_s \cap E_T$ of the graph repeats over time.
+In the unrolled st-graph, the ndoes at a given time step t are connected with undirected spatio-temporal edge $e = (u,v) \in E_s$ and the nodes at adjacent time steps ( node $u$ at time $t$ and $v$ at time $t + 1$) are connected with undirected temporal edge iff $(u,v) \in E_T$.
+\item Given a st-graph and the feature vectors associated with the nodes $x_v^t$ and edges $x_e^t$, the goal is to predict the node labels (or real value vectors) $y_v^t$ at each time step t.
+Label $y_v^t$ is afffectedby both its node and its interactions with other nodes (edges), leading to an overall complex system.
+\item Here : derive SRNN structure from the factor-graph representation of st-graph.
+The factor graph has a factor function $\Psi_v(y_v, x_v)$ for each node and a pairwise factor $\Psi_e(y_{e(1)}, y_{e(2)}, x_e)$ for each edge.
+\item Sharing factors between nodes : Each factor has parameters that needs to be learned. Semantically similar nodes can optionally share factors.
+\item Partition the nodes as $C_v = \{V_1, ...
+, V_P\}$ where $V_P$ is a set of semantically similar nodes and they all use the same node factor $\Psi_{V_p}$.
+Similaryly for edges.
+For modeling flexibility the edge factors are note shared across the edges in $E_s$ and $E_T$.
+\item To predict teh label of the node $v \in V_P$ : consider node factor, edge factors connected to v in the factor graph.
+Formally the node factor and edge factor are neighbors if there exists a node v such taht it connects to both in the factor graph.
+\end{itemize}
+
+\subsubsection{Structural RNN from spatio-temporal graphs}
+\begin{itemize}
+\item Represent each factor with an RNN.
+As such there are nodeRNNs $R_{V_p}$  and edgeRNNs $R_{E_m}$ and they are connected iff they are neighbors in the original st-graph, outputs a bipartite graph $G = (R_{E_m}, R_{V_p}, E_R)$.
+\item The predictions of nodeRNNs interact through edgeRNNs.
+\end{itemize}
+
+\subsubsection{Training structural-RNN architecture}
+\begin{itemize}
+\item The nodeRNN at each time step concatenates the node feature $x_v^t$ and the outsputs of edgeRNNs it is connected to and predictst hte node label.
+At the time of training the errors int eh prediction are back propagated through the nodeRNN and edge RN involved during the forward pass.
+\item Parameter sharing and strucutred feature space
+\end{itemize}
+
 \bibliography{../Daily_progress/papers.bib}

### 2017-08-29 code/graph_cnn/coarsening.py
Started coding graph cnn

@@ -1,0 +1,269 @@
+import numpy as np
+import scipy.sparse
+
+
+def coarsen(A, levels, self_connections=False):
+    """
+    Coarsen a graph, represented by its adjacency matrix A, at multiple
+    levels.
+    """
+    graphs, parents = metis(A, levels)
+    perms = compute_perm(parents)
+
+    for i, A in enumerate(graphs):
+        M, M = A.shape
+
+        if not self_connections:
+            A = A.tocoo()
+            A.setdiag(0)
+
+        if i < levels:
+            A = perm_adjacency(A, perms[i])
+
+        A = A.tocsr()
+        A.eliminate_zeros()
+        graphs[i] = A
+
+        Mnew, Mnew = A.shape
+        print('Layer {0}: M_{0} = |V| = {1} nodes ({2} added),'
+              '|E| = {3} edges'.format(i, Mnew, Mnew-M, A.nnz//2))
+
+    return graphs, perms[0] if levels > 0 else None
+
+
+def metis(W, levels, rid=None):
+    """
+    Coarsen a graph multiple times using the METIS algorithm.
+
+    INPUT
+    W: symmetric sparse weight (adjacency) matrix
+    levels: the number of coarsened graphs
+
+    OUTPUT
+    graph[0]: original graph of size N_1
+    graph[2]: coarser graph of size N_2 < N_1
+    graph[levels]: coarsest graph of Size N_levels < ... < N_2 < N_1
+    parents[i] is a vector of size N_i with entries ranging from 1 to N_{i+1}
+        which indicate the parents in the coarser graph[i+1]
+    nd_sz{i} is a vector of size N_i that contains the size of the supernode in the graph{i}
+
+    NOTE
+    if "graph" is a list of length k, then "parents" will be a list of length k-1
+    """
+
+    N, N = W.shape
+    if rid is None:
+        rid = np.random.permutation(range(N))
+    parents = []
+    degree = W.sum(axis=0) - W.diagonal()
+    graphs = []
+    graphs.append(W)
+    # supernode_size = np.ones(N)
+    # nd_sz = [supernode_size]
+    # count = 0
+
+    # while N > maxsize:
+    for _ in range(levels):
+
+        # count += 1
+
+        # CHOOSE THE WEIGHTS FOR THE PAIRING
+        # weights = ones(N,1)       # metis weights
+        weights = degree            # graclus weights
+        # weights = supernode_size  # other possibility
[…]

### 2017-08-29 code/graph_cnn/graph_main.py

@@ -1,0 +1,60 @@
+import networkx as nx
+import numpy as np
+import scipy.spatial.distance as spd
+import matplotlib.pyplot as plt
+import pdb
+import coarsening as crs
+
+
+def graph_from_X(train_data_column, k=4, metric='euclidean'):
+    d = spd.pdist(train_data_column, metric)
+    adj_actual = spd.squareform(d)
+    adj_k = np.zeros(adj_actual.shape, np.float32)
+    for row in range(adj_k.shape[0]):
+        orig_row = adj_actual[row, :]
+        topk_ids = np.argsort(orig_row)[:k]
+        # pdb.set_trace()
+        adj_k[row, topk_ids] = orig_row[topk_ids]
+    G = nx.from_numpy_matrix(adj_k)
+    return G, adj_k
+
+
+if __name__ == '__main__':
+    # first try with random data generation
+    d = 100    # Dimensionality.
+    n = 10000  # Number of samples.
+    c = 5      # Number of feature communities.
+
+    # Data matrix, structured in communities (feature-wise).
+    X = np.random.normal(0, 1, (n, d)).astype(np.float32)
+    X += np.linspace(0, 1, c).repeat(d // c)
+
+    # Noisy non-linear target.
+    w = np.random.normal(0, .02, d)
+    t = X.dot(w) + np.random.normal(0, .001, n)
+    t = np.tanh(t)
+    # plt.figure(figsize=(15, 5))
+    # plt.plot(t, '.')
+
+    # Classification.
+    y = np.ones(t.shape, dtype=np.uint8)
+    y[t > t.mean() + 0.4 * t.std()] = 0
+    y[t < t.mean() - 0.4 * t.std()] = 2
+    # print('Class imbalance: ', np.unique(y, return_counts=True)[1])
+
+    # split into train, test, validation
+
+    n_train = n // 2
+    n_val = n // 10
+
+    X_train = X[:n_train]
+    X_val = X[n_train:n_train+n_val]
+    X_test = X[n_train+n_val:]
+
+    y_train = y[:n_train]
+    y_val = y[n_train:n_train+n_val]
+    y_test = y[n_train+n_val:]
+    # Note : np.array().T gives the transpose
+    G, adj_k = graph_from_X(X_train.T, k=10)
+    # plt.spy(adj_k, markersize=2, color='black')
+    # plt.show()

### 2017-08-29 code/graph_cnn/coarsening.py
need to rectify silly errors

@@ -1,6 +1,6 @@
 import numpy as np
 import scipy.sparse
-
+import networkx as nx
 
 def coarsen(A, levels, self_connections=False):
     """
@@ -8,6 +8,7 @@ def coarsen(A, levels, self_connections=False):
     levels.
     """
     graphs, parents = metis(A, levels)
+    graphs_new = []
     perms = compute_perm(parents)
 
     for i, A in enumerate(graphs):
@@ -23,6 +24,7 @@ def coarsen(A, levels, self_connections=False):
         A = A.tocsr()
         A.eliminate_zeros()
         graphs[i] = A
+        # graphs_new.append(nx.from_numpy_matrix(A))
 
         Mnew, Mnew = A.shape
         print('Layer {0}: M_{0} = |V| = {1} nodes ({2} added),'

### 2017-08-29 code/graph_cnn/graph_main.py

@@ -16,7 +16,7 @@ def graph_from_X(train_data_column, k=4, metric='euclidean'):
         # pdb.set_trace()
         adj_k[row, topk_ids] = orig_row[topk_ids]
     G = nx.from_numpy_matrix(adj_k)
-    return G, adj_k
+    return G
 
 
 if __name__ == '__main__':
@@ -55,6 +55,12 @@ if __name__ == '__main__':
     y_val = y[n_train:n_train+n_val]
     y_test = y[n_train+n_val:]
     # Note : np.array().T gives the transpose
-    G, adj_k = graph_from_X(X_train.T, k=10)
-    # plt.spy(adj_k, markersize=2, color='black')
+    G = graph_from_X(X_train.T, k=10)
+    adj_k = nx.adjacency_matrix(G)
+    # plt.spy(nx.adjacency_matrix(G), markersize=2, color='black')
     # plt.show()
+
+    graphs, perm = crs.coarsen(adj_k, levels=3, self_connections=False)
+    X_train1 = crs.perm_data(X_train, perm)
+    X_val1 = crs.perm_data(X_val, perm)
+    X_test1 = crs.perm_data(X_test, perm)

### 2017-08-29 code/graph_cnn/coarsening.py
All is correct upto this point, normal graph techniques working
time for graph convolution using pytorch

@@ -24,13 +24,13 @@ def coarsen(A, levels, self_connections=False):
         A = A.tocsr()
         A.eliminate_zeros()
         graphs[i] = A
-        # graphs_new.append(nx.from_numpy_matrix(A))
-
+        graphs_new.append(nx.from_numpy_matrix(A.todense()))
+        # G = nx.from_numpy_matrix(A.todense())
         Mnew, Mnew = A.shape
         print('Layer {0}: M_{0} = |V| = {1} nodes ({2} added),'
               '|E| = {3} edges'.format(i, Mnew, Mnew-M, A.nnz//2))
 
-    return graphs, perms[0] if levels > 0 else None
+    return graphs_new, perms[0] if levels > 0 else None
 
 
 def metis(W, levels, rid=None):

### 2017-08-29 code/graph_cnn/graph_main.py

@@ -19,6 +19,34 @@ def graph_from_X(train_data_column, k=4, metric='euclidean'):
     return G
 
 
+def lapl_of_graph(G, normalized=True):
+    if not normalized:
+        return nx.laplacian_matrix(G)
+    else:
+        return nx.normalized_laplacian_matrix(G)
+
+
+def plot_spectrum(L, algo='eig'):
+    """Plot the spectrum of a list of multi-scale Laplacians L."""
+
+    def sort(lamb, U):
+        idx = lamb.argsort()
+        return lamb[idx], U[:, idx]
+    # Algo is eig to be sure to get all eigenvalues.
+
+    plt.figure(figsize=(17, 5))
+    for i, lap in enumerate(L):
+        lamb, U = np.linalg.eig(lap.toarray())
+        lamb, U = sort(lamb, U)
+        step = 2**i
+        x = range(step//2, L[0].shape[0], step)
+        lb = 'L_{} spectrum in [{:1.2e}, {:1.2e}]'.format(i, lamb[0], lamb[-1])
+        plt.plot(x, lamb, '.', label=lb)
+    plt.legend(loc='best')
+    plt.xlim(0, L[0].shape[0])
+    plt.ylim(ymin=0)
+
+
 if __name__ == '__main__':
     # first try with random data generation
     d = 100    # Dimensionality.
@@ -64,3 +92,9 @@ if __name__ == '__main__':
     X_train1 = crs.perm_data(X_train, perm)
     X_val1 = crs.perm_data(X_val, perm)
     X_test1 = crs.perm_data(X_test, perm)
+
+    # Right now the data that I have is permuted
+    # and the pooling is equivalent to 1D pooling
+    L = [lapl_of_graph(A, normalized=True) for A in graphs]
+    plot_spectrum(L)
+    # ==========All is correct upto this point ==========

### 2017-08-31 Work_report/Presentation/GCN/gcn_presentation.tex
Adding template code for latex presentation

\documentclass{beamer}
\usetheme{Boadilla}

\title{My Presentation}
\subtitle{Using Beamer}
\author{Joe Bloggs}
\institute{University of ShareLaTeX}
\date{\today}

\begin{document}
% document goes here

\begin{frame}
\titlepage
\end{frame}

\section{Section 1}
\subsection{sub a}

\begin{frame}
\frametitle{Title}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
\end{frame}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}

\subsection{sub b}
\begin{frame}
\frametitle{List}
\begin{itemize}
\item Point A
\item Point B
\begin{itemize}
\item part 1
\item part 2
\end{itemize}
\item Point C
\item Point D
\end{itemize}
\end{frame}

\section{section 2}
\begin{frame}
  \frametitle{Enumerate}
  \begin{enumerate}[I]
  \item Point A
  \item Point B
    \begin{enumerate}[i]
    \item part 1
    \item part 2
    \end{enumerate}
  \item Point C
  \item Point D
  \end{enumerate}

\end{frame}

\subsection{sub A}
\begin{frame}
\frametitle{Using Columns}
\begin{columns}
\column{0.5\textwidth}
\begin{description}
\item[API] Application Programming Interface
\item[LAN] Local Area Network
\item[ASCII] American Standard Code for Information Interchange
\end{description}

\column{0.5\textwidth}
\begin{description}
\item[API] Application Programming Interface
\item[LAN] Local Area Network
\item[ASCII] American Standard Code for Information Interchange
\end{description}

\end{columns}
\end{frame}

\end{document}

### 2017-08-31 code/graph_cnn/cnn_classes.py

@@ -1,0 +1,13 @@
+# import torch
+import numpy as np
+import sklearn
+
+
+class base_model(object):
+
+    def __init__(self):
+        self.regularizers = []
+
+def predict(self, data, labels=None):
+    loss = 0
+    size = data.shape[0]

### 2017-08-31 Work_report/Presentation/GCN/gcn_presentation.tex
Partial presentation on the way

@@
 \usetheme{Boadilla}
+% \usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
+\usepackage[utf8]{inputenc}
+\usepackage{graphicx}
+\usepackage{parskip}
+\usepackage{pdflscape}
+\usepackage{listings}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{amssymb}
 
-\title{My Presentation}
-\subtitle{Using Beamer}
-\author{Joe Bloggs}
-\institute{University of ShareLaTeX}
+\title{Graph Convolution Networks}
+% \subtitle{Using Beamer}
+\author{Arka Sadhu}
+\institute{IIT Bombay}
 \date{\today}
@@
 
-\section{Section 1}
-\subsection{sub a}
-
-\begin{frame}
-\frametitle{Title}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-\end{frame}
-
 \begin{frame}
@@
 
-\subsection{sub b}
+\section{Graph Convolutional Networks}
+\subsection{Why GCN}
 \begin{frame}
-\frametitle{List}
+  \frametitle{Introduction to Graph Convolutional Networks}
   \begin{itemize}
-\item Point A
-\item Point B
-\begin{itemize}
-\item part 1
-\item part 2
-\end{itemize}
-\item Point C
-\item Point D
+  \item <1-> CNN are extremely efficient architectures for image and audio classification tasks.
+  \item <1-> But CNN donot directly generalize to irregular domains such as graph.
+  \item <2-> Want to generalize CNN to Graphs.
+  % \item <3-> Some applications would be spatio-temporal
   \end{itemize}
@@
 
-\section{section 2}
+\subsection{How to extend convolution to graphs?}
 \begin{frame}
-  \frametitle{Enumerate}
-  \begin{enumerate}[I]
-  \item Point A
-  \item Point B
-    \begin{enumerate}[i]
-    \item part 1
-    \item part 2
-    \end{enumerate}
-  \item Point C
-  \item Point D
-  \end{enumerate}
+  \frametitle{Extending Convolutional to Graphs}
+  There are two main approaches
+  \begin{itemize}
+  \item <1->Spatial Approach :\\
+    Generalization of CNN in the spatial domain itself.
+    \begin{itemize}
+    \item <2-> Learning Convolutional Neural Networks for Graphs [ICML 2016].\cite{DBLP:journals/corr/NiepertAK16}
+    \end{itemize}
+  \item <3-> Spectral Approach :\\
+    Using the frequency characterization of CNN and using that to generalize to Graphical domain
+    \begin{itemize}
+    \item <4->Spectral Networks and Deep Locally Connected Networks on Graphs [ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
+    \item <4->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [NIPS 2016] % \cite{DBLP:journals/corr/DefferrardBV16}
+    \item <4->Semi-Supervised Classification with Graph Convolutional Networks [ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\section{Spatial Approach}
+\begin{frame}
+  \frametitle{Direct extension of convolution}
 
@@
 
-\subsection{sub A}
-\begin{frame}
-\frametitle{Using Columns}
-\begin{columns}
-\column{0.5\textwidth}
-\begin{description}
-\item[API] Application Programming Interface
-\item[LAN] Local Area Network
-\item[ASCII] American Standard Code for Information Interchange
-\end{description}
+% \section{Section 1}
+% \subsection{sub a}
 
-\column{0.5\textwidth}
-\begin{description}
-\item[API] Application Programming Interface
-\item[LAN] Local Area Network
-\item[ASCII] American Standard Code for Information Interchange
-\end{description}
+% \begin{frame}
+% \frametitle{Title}
+% Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+% \end{frame}
 
-\end{columns}
-\end{frame}
+% \section{sub b}
+% \begin{frame}
+% \frametitle{List}
+% \begin{itemize}
+% \item<1-> Point A
+% \item<2-> Point B
+% \begin{itemize}
+% \item part 1
+% \item part 2
+% \end{itemize}
+% \item <3->Point C
+% \item <4->Point D
+% \end{itemize}
+% \end{frame}
+
+% \section{section 2}
+% \begin{frame}
+%   \frametitle{Enumerate}
+%   \begin{enumerate}[I]
+%   \item Point A
+%   \item Point B
+%     \begin{enumerate}[i]
+%     \item part 1
+%     \item part 2
+%     \end{enumerate}
+%   \item Point C
+%   \item Point D
+%   \end{enumerate}
+
+% \end{frame}
+
+% \subsection{sub A}
+% \begin{frame}
+% \frametitle{Using Columns}
+% \begin{columns}
+% \column{0.5\textwidth}
+% \begin{description}
+% \item[API] Application Programming Interface
+% \item[LAN] Local Area Network
+% \item[ASCII] American Standard Code for Information Interchange
+% \end{description}
+
+% \column{0.5\textwidth}
+% \begin{description}
+% \item[API] Application Programming Interface
+% \item[LAN] Local Area Network
+% \item[ASCII] American Standard Code for Information Interchange
+% \end{description}
+
+% \end{columns}
+% \end{frame}
+
+\bibliography{ref.bib}
+\bibliographystyle{ieeetr}
 

### 2017-08-31 Work_report/Presentation/GCN/gcn_presentation.tex
I think at least 50% of the presentation is complete

@@
 \usepackage{amssymb}
+
+\AtBeginSubsection[
+  {\frame<beamer>{\frametitle{Outline}
+    \tableofcontents[currentsection,currentsubsection]}}%
+]%
+{
+  \frame<beamer>{
+    \frametitle{Outline}
+    \tableofcontents[currentsection,currentsubsection]}
+}
 
@@
 \section{Graph Convolutional Networks}
+
 \subsection{Why GCN}
@@
   \item <2-> Want to generalize CNN to Graphs.
+  \item <3-> Non-trivial because the distances are non-euclidean.
   % \item <3-> Some applications would be spatio-temporal
@@
     \begin{itemize}
-    \item <4->Spectral Networks and Deep Locally Connected Networks on Graphs [ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
-    \item <4->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [NIPS 2016] % \cite{DBLP:journals/corr/DefferrardBV16}
-    \item <4->Semi-Supervised Classification with Graph Convolutional Networks [ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
+    \item <4->Spectral Networks and Deep Locally Connected Networks on Graphs [Bruna et al. ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
+    \item <4->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [Defferrard et al. NIPS 2016] (will be the main focus) % \cite{DBLP:journals/corr/DefferrardBV16}
+    \item <4->Semi-Supervised Classification with Graph Convolutional Networks [Kipf et al. ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
     \end{itemize}
@@
 \begin{frame}
-  \frametitle{Direct extension of convolution}
-
+  \frametitle{Limitations of Spatial Approach}
+  \begin{itemize}
+  \item Can't exactly define a neighborhood because the distances are not uniform.
+  \item Ordering of nodes is problem specific.
+  \end{itemize}
+  Hence for the remainder we discuss the Spectral Approach
 \end{frame}
 
-% \section{Section 1}
-% \subsection{sub a}
+\section{Spectral Approach}
+\subsection{Basics of Spectral Approach}
+\begin{frame}
+  \frametitle{A Basic Formulation}
+  \begin{itemize}
+  \item Convolution in spectral (Fourier) domain is point wise multiplication.
+  \item Fourier Basis is defined as the eigen basis of the laplacian operator.
+  \item Can use Laplacian of a graph.
+  \end{itemize}
+\end{frame}
 
-% \begin{frame}
-% \frametitle{Title}
-% Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-% \end{frame}
+\subsection{Problem Formulation}
+\begin{frame}
+  \frametitle{Defining the Problem on Graphs}
+  \begin{itemize}
+  \item <1-> A feature description $x_i$ for every node $i$; summarized in a $N x D$ feature matrix $X$ ($N$ : number of nodes, $D$ : number of input features)
+  \item <2-> Adjacency Matrix $A$.
+  \item <3-> Node level output $Z$ (an $N x F$ feature matrix, where $F$ = number of output features per node).
+  \end{itemize}
+\end{frame}
 
-% \section{sub b}
-% \begin{frame}
-% \frametitle{List}
-% \begin{itemize}
-% \item<1-> Point A
-% \item<2-> Point B
-% \begin{itemize}
-% \item part 1
-% \item part 2
-% \end{itemize}
-% \item <3->Point C
-% \item <4->Point D
-% \end{itemize}
-% \end{frame}
+\subsection{Graph Laplacian}
+\begin{frame}
+  \frametitle{Brief overview of Graph Laplacian}
+  Let $T$ denote the diagonal matrix with ($v$,$v$)-th entry having value $d_v$ : degree of vertex $v$.
+  % $$L(u,v) = $$
+  Define L-matrix as
+  \[
+    L(u,v) =
+    \begin{cases}
+      d_v &\quad\text{if u = v}\\
+      -1 &\quad\text{if u and v are adjacent}\\
+      0 &\quad \text{otherwise}\\
+    \end{cases}
+  \]
+  And the Laplacian of the graph as
+  \[
+    \mathcal{L}(u,v) =
+    \begin{cases}
+      1 &\quad\text{if u = v}\\
+      -\frac{1}{\sqrt{d_ud_v}} &\quad\text{if u and v are adjacent}\\
+      0 &\quad \text{otherwise}\\
+    \end{cases}
+  \]
+\end{frame}
 
-% \section{section 2}
-% \begin{frame}
-%   \frametitle{Enumerate}
-%   \begin{enumerate}[I]
-%   \item Point A
-%   \item Point B
-%     \begin{enumerate}[i]
-%     \item part 1
-%     \item part 2
-%     \end{enumerate}
-%   \item Point C
-%   \item Point D
-%   \end{enumerate}
+\begin{frame}
+  \frametitle{Graph Laplacian (contd.)}
+  $$\mathcal{L} = T^{-1/2}LT^{1/2}$$
+  With the convention $T^{-1}(v,v) = 0$ for $d_v = 0$.\\
+  When G is k-regular,
+  $$\mathcal{L} = I - \frac{1}{k}A$$
+  For a general graph
+  $$\mathcal{L} = I - T^{-1/2}AT^{1/2}$$
+\end{frame}
 
-% \end{frame}
+\section{CNN on Graphs with Fast Localized Spectral Filtering}
+\subsection{Learning fast localized Spectral filters}
+\begin{frame}
+  \frametitle{Graph Fourier Transform}
+  \begin{itemize}
+  \item Laplcian of the graph is real symmetric positive semidefinite, and thus can be written as
+    $$L = U \Lambda U^{T}$$
+  \item Here $U = [u_0 .... u_{n-1}]$ is the fourier basis and $\Lambda = diag([\lambda_0...\lambda_{n-1}])$ are ordered real non-negative eigen values.
+  \item Graph Fourier Transform of a signal $x$ is $\hat{x} = U^{T}x$.
+  \end{itemize}
+\end{frame}
 
-% \subsection{sub A}
-% \begin{frame}
-% \frametitle{Using Columns}
-% \begin{columns}
-% \column{0.5\textwidth}
-% \begin{description}
-% \item[API] Application Programming Interface
-% \item[LAN] Local Area Network
-% \item[ASCII] American Standard Code for Information Interchange
-% \end{description}
+\begin{frame}
+  \frametitle{Spectral filtering of graph signals}
+  \begin{itemize}
+  \item Defining convolution on graphs
+    $$ x *_{G} y = U((U^T x) \odot (U^T y))$$
+  \item Filtering by $g_{\theta}$
+    $$ y = g_{\theta}(L)x = g_{\theta}(U \Lambda U^{T})x = Ug_{\theta}(\Lambda) U^T x $$
+  \item A non-parametric filter (all parameters free) would be defined as
+    $$g_{\theta}(\Lambda) = diag(\theta)$$
+  \end{itemize}
+\end{frame}
 
-% \column{0.5\textwidth}
-% \begin{description}
-% \item[API] Application Programming Interface
-% \item[LAN] Local Area Network
-% \item[ASCII] American Standard Code for Information Interchange
-% \end{description}
+\begin{frame}
+  \frametitle{Polynomial Parametrization}
+  \begin{itemize}
+  \item   Problem with non-parametric filters is that not localized (we want something like k-neighborhood) and therefore their learning complexity becomes $O(n)$.
+This can be overcomed with use of a Polynomial filter
+    $$g_{\theta}(\Lambda) = \sum_{k = 0}^{K-1}\theta_k\Lambda^k$$
+  \item The advantage we gain here is that nodes which are at a distance greater than $K$ away from the node $i$, at which the filter is applied, are not affected. Hence we have gained localization.
+  \end{itemize}
+\end{frame}
 
-% \end{columns}
-% \end{frame}
+\begin{frame}
+  \frametitle{Recursive formulation for fast filtering}
+  \begin{itemize}
+  \item Still cost to filter is high $O(n^2)$ because of multiplication with $U$ matrix.
+  \item Therefore use recurrence relation of chebyshev polynomial instead.
+    $$g_{\theta}(\Lambda) = \sum_{k=0}^{K-1}\theta_k T_K(\tilde{\Lambda})$$
+    Here $\tilde{\Lambda}$ is scaled between $[-1,1]$.
+  \item This allows us to compute $\bar{x_k} = T_K{\tilde{L}}x$. And Therefore
+    $$ y = g_{\theta}(L)x = [\bar{x_0}...\bar{x_{k-1}}]\theta$$
+  \item The cost is now $O(K|E|)$
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Learning filters}
+  \begin{itemize}
+  \item Trivial to show that backprop calculation can be done efficiently.
+  \end{itemize}
+\end{frame}
 

### 2017-08-31 Work_report/Presentation/GCN/gcn_presentation.tex
Done a little more, need to add quantitative and qualitative results
Possibly some pictures

@@
 \end{frame}
+\section{Spectral Networks and Deep Locally Connected Networks on Graphs}
+\begin{frame}
+  \frame{Spectral Network Approach}
+  \begin{itemize}
+  \item Mentions the use of both spatial and spectral construction.
+  \item For the spectral part uses a spline and has k control points for it.
+    $$g_{\theta}(\Lambda) = B\theta$$
+    Here $B$ is the cubic B-spline basis and $\theta$ is a vector of control points.
+  \item The datasets used (created) are quite interesting. Subsampled MNIST and MNIST on sphere to show how spectral networks can be used on graphs.
+  \end{itemize}
+\end{frame}
 
@@
 
+\subsection{Coarsening and Pooling}
+\begin{frame}
+  \frametitle{Graph Coarsening and Pooling}
+  \begin{itemize}
+  \item Require efficient mechanism for pooling. Graph clustering as such is NP-hard and some approximations must be made.
+  \item The paper uses Graclus algorithm for coarsening, and uses an intelligent way of rearranging the nodes [creating a balanced binary tree from the remaining singleton and fake nodes] so that the pooling now becomes equivalent to pooling a regular 1D signal.
+  \end{itemize}
+\end{frame}
+
+\subsection{Results on MNIST}
+\begin{frame}
+  \frametitle{MNIST results}
+  \begin{itemize}
+  \item Achieves close to classical CNN accuracy.
+  \item Pictures to be added.
+  \end{itemize}
+\end{frame}
+
 \bibliography{ref.bib}

### 2017-08-31 Work_report/Presentation/GCN/gcn_presentation.tex
I think presentation turned out decent enough
hoping that the presentation would go nice. But do good things always happen

@@
 
-\AtBeginSubsection[
-  {\frame<beamer>{\frametitle{Outline}
-    \tableofcontents[currentsection,currentsubsection]}}%
-]%
+\mode<presentation>{
+    \AtBeginSection[]
     {
-  \frame<beamer>{
-    \frametitle{Outline}
-    \tableofcontents[currentsection,currentsubsection]}
+    \begin{frame}[allowframebreaks]{Outline}
+    \tableofcontents[currentsection]
+    \end{frame}
     }
+}
+% \AtBeginSubsection[
+%   {\frame<beamer>{\frametitle{Outline}
+%     \tableofcontents[currentsection,currentsubsection]}}%
+% ]%
+% {
+%   \frame<beamer>{
+%     \frametitle{Outline}
+%     \tableofcontents[currentsection,currentsubsection]}
+% }
 
@@
 
-\subsection{Why GCN}
+% \subsection{Why GCN}
 \begin{frame}
@@
 
-\subsection{How to extend convolution to graphs?}
+% \subsection{How to extend convolution to graphs?}
 \begin{frame}
@@
 
-\section{Spatial Approach}
+\section{Problems with Spatial Approach}
 \begin{frame}
@@
 \section{Spectral Approach}
-\subsection{Basics of Spectral Approach}
+% \subsection{Basics of Spectral Approach}
 \begin{frame}
@@
 
-\subsection{Problem Formulation}
+% \subsection{Problem Formulation}
 \begin{frame}
@@
   \item <3-> Node level output $Z$ (an $N x F$ feature matrix, where $F$ = number of output features per node).
+  \item <4-> Every neural network can then be written as a non-linear function.
+    $$H^{(l+1)} = f(H^{l}, A)$$
   \end{itemize}
@@
 
-\subsection{Graph Laplacian}
+% \subsection{Graph Laplacian}
 \begin{frame}
@@
 \begin{frame}
-  \frame{Spectral Network Approach}
+  \frametitle{Spectral Networks and Deep Locally Connected Networks on Graphs}
   \begin{itemize}
@@
 
-\subsection{Results on MNIST}
+% \subsection{Results on MNIST}
 \begin{frame}
@@
 
-\bibliography{ref.bib}
-\bibliographystyle{ieeetr}
+\section{Semi-Supervised Classification with Graph Convolutional Networks}
+\begin{frame}
+  \frametitle{Fast approximate convolutions on the graph}
+  \begin{itemize}
+  \item Layerwise propagation rule as
+    $$H^{(l+1)} = \sigma(\tilde{D}^{-1/2}\tilde{A}\tilde{D}^{-1/2}H^{(l)}W^{(l)})$$
+    Here $\tilde{A} = A + I_N$ the adjacency matrix with added self-loops. $\tilde{D}$ is the degree matrix.
+  \item In the chebyshev approximation, limit to $K=1$ and therefore the layer-wise convolution operation is linear function of the laplacian.
+  \item Experimentally shows 2-3 layered GCN can effectively learn standard graph problems.
+Specifically it does decently well in the unsupervised case, and significantly good in the semi-supervised setting.
+  \end{itemize}
+\end{frame}
+
+\section{Limitations of Graph Convolutional Networks}
+\begin{frame}
+  \frametitle{Limitations}
+  \begin{itemize}
+  \item We would like to model a network which doesn't require a rectangular input size and therefore be able to accomodate superpixels.
+In theory this should be possible, but there are a few points that we need to keep in mind.
+    \begin{itemize}
+    \item Graph doesn't have orientation.
+There is no sense of up, down, left or right.
+The filters are rotationally invariant.
+This can be both advantageous as well as disadvantageous depending on the set-up of the problem.
+Spatial Transformer Networks learn the invariance to rotation as well as generic warping.
+But there is always the problem of '6' and '9' because they are equivalent in modulo rotation.
+    \item The filters are not directly transferable to another graph (because of the graph laplacian).
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+% \bibliography{ref.bib}
+% \bibliographystyle{ieeetr}
 

### 2017-09-01 Work_report/Presentation/GCN/gcn_presentation.tex
Some updates to the gcn presentation

@@
 \usepackage{amssymb}
-
+\usepackage{multirow}
 \mode<presentation>{
@@
   \item Achieves close to classical CNN accuracy.
-  \item Pictures to be added.
+    % \item Pictures to be added.
+    \begin{table}[H]
+      \centering
+      \caption{MNIST performance}
+      \label{t:mn_perf}
+      \begin{tabular}{|l|l|l|l|l|l|l|l|}
+        \hline
+        \multicolumn{2}{|l|}{accuracy} & \multicolumn{2}{l|}{loss} & \multirow{2}{*}{name}       \\ \cline{1-4}
+        test           & train         & test        & train       &                             \\ \hline
+        98.87          & 99.62         & 1.02e+00    & 9.99e-01    & cgconv\_cgconv\_fc\_softmax \\ \hline
+        98.00          & 99.26         & 6.52e-02    & 2.77e-02    & cgconv\_softmax             \\ \hline
+        96.75          & 96.78         & 1.12e+00    & 1.12e+00    & fgconv\_fgconv\_fc\_softmax \\ \hline
+        95.91          & 95.50         & 1.44e-01    & 1.53e-01    & fgconv\_softmax             \\ \hline
+        97.66          & 97.79         & 1.09e+00    & 1.08e+00    & sgconv\_sgconv\_fc\_softmax \\ \hline
+        96.95          & 97.27         & 1.03e-01    & 9.46e-02    & sgconv\_softmax             \\ \hline
+        92.18          & 92.47         & 3.14e-01    & 3.14e-01    & softmax                     \\ \hline
+      \end{tabular}
+    \end{table}
 \end{itemize}
@@
 
+\begin{frame}
+  \frametitle{Accuracy and Loss Plots}
+  \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.38]{images/accuracy_plot.png}
+    \caption{Accuracy and Loss function plot}
+    \label{fig:acl_mnist}
+  \end{figure}
+
+\end{frame}
 \section{Semi-Supervised Classification with Graph Convolutional Networks}

### 2017-09-01 Work_report/Presentation/GCN/gcn_presentation.tex
Final changes made, lets see how it goes

@@
   \begin{itemize}
-  \item <1-> CNN are extremely efficient architectures for image and audio classification tasks.
-  \item <1-> But CNN donot directly generalize to irregular domains such as graph.
-  \item <2-> Want to generalize CNN to Graphs.
-  \item <3-> Non-trivial because the distances are non-euclidean.
+  \item  CNN are extremely efficient architectures for image and audio classification tasks.
+  \item  But CNN donot directly generalize to irregular domains such as graph.
+  \item  Want to generalize CNN to Graphs.
+  \item  Non-trivial because the distances are non-euclidean.
   % \item <3-> Some applications would be spatio-temporal
@@
     \begin{itemize}
-    \item <2-> Learning Convolutional Neural Networks for Graphs [ICML 2016].\cite{DBLP:journals/corr/NiepertAK16}
+    \item <1-> Learning Convolutional Neural Networks for Graphs [ICML 2016].% \cite{DBLP:journals/corr/NiepertAK16}
     \end{itemize}
-  \item <3-> Spectral Approach :\\
+  \item <2-> Spectral Approach :\\
     Using the frequency characterization of CNN and using that to generalize to Graphical domain
     \begin{itemize}
-    \item <4->Spectral Networks and Deep Locally Connected Networks on Graphs [Bruna et al. ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
-    \item <4->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [Defferrard et al. NIPS 2016] (will be the main focus) % \cite{DBLP:journals/corr/DefferrardBV16}
-    \item <4->Semi-Supervised Classification with Graph Convolutional Networks [Kipf et al. ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
+    \item <2->Spectral Networks and Deep Locally Connected Networks on Graphs [Bruna et al. ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
+    \item <2->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [Defferrard et al. NIPS 2016] (will be the main focus) % \cite{DBLP:journals/corr/DefferrardBV16}
+    \item <2->Semi-Supervised Classification with Graph Convolutional Networks [Kipf et al. ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
     \end{itemize}
@@
   \begin{itemize}
-  \item <1-> A feature description $x_i$ for every node $i$; summarized in a $N x D$ feature matrix $X$ ($N$ : number of nodes, $D$ : number of input features)
-  \item <2-> Adjacency Matrix $A$.
-  \item <3-> Node level output $Z$ (an $N x F$ feature matrix, where $F$ = number of output features per node).
-  \item <4-> Every neural network can then be written as a non-linear function.
+  \item A feature description $x_i$ for every node $i$; summarized in a $N x D$ feature matrix $X$ ($N$ : number of nodes, $D$ : number of input features)
+  \item Adjacency Matrix $A$.
+  \item  Node level output $Z$ (an $N x F$ feature matrix, where $F$ = number of output features per node).
+  \item  Every neural network can then be written as a non-linear function.
     $$H^{(l+1)} = f(H^{l}, A)$$

### 2017-09-06 code/graph_cnn/checking_out_graphs.py
Finally got access to vip lab comp wo ho!

@@ -1,0 +1,23 @@
+import scipy.io as sio
+import skimage.io as skio
+
+
+class helper_mat_file(object):
+    def __init__(self, mat_file, img_file):
+        self.img = img_file
+        self.seg_img = mat_file['segImgI']
+        self.adj_graph = mat_file['graphI']
+        self.sI = mat_file['sI']
+        self.bg_prob = mat_file['bgProb']
+        self.segments = mat_file['segmentsI']
+        return
+
+
+if __name__ == '__main__':
+    print('Starting to Load Mat files')
+
+    mat_file = sio.loadmat(
+        '../../data/image_coseg_avik_data/weizmann_horse_db/seg200/horse001.mat')
+    img_file = skio.imread('../../data/image_coseg_avik_data/weizmann_horse_db/rgb/horse001.jpg')
+    h = helper_mat_file(mat_file, img_file)
+    # skio.imshow(img_file)

### 2017-09-06 code/graph_cnn/cnn_classes.py

@@ -1,13 +1,27 @@
 # import torch
 import numpy as np
 import sklearn
+import networkx as nx
 
 
-class base_model(object):
+class gcn_layer(object):
+    def __init__(self, adj_graph, is_sparse=False):
+        # for the time being assuming that
+        # one graph is enough to represent one layer
+        if is_sparse:
+            self.G = nx.from_scipy_sparse_matrix(adj_graph)
+        else:
+            self.G = nx.from_numpy_matrix(adj_graph)
+        self.sparse_adj_mat = self.G.adjacency_matrix()
+        self.coarse_graphs = list()
 
-    def __init__(self):
-        self.regularizers = []
+    def coarsen(self):
+        # Coarsen a graph
 
-def predict(self, data, labels=None):
-    loss = 0
-    size = data.shape[0]
+    def metis(self, levels):
+        # Coarsen a graph multiple times using the Metis algorithm
+        # levels is the number of coarsened graphs
+        self.coarse_graphs.append(G)
+
+        for i in range(levels):
+            # Need to choose the weights for pairing

### 2017-09-06 code/graph_cnn/coarsening.py

@@ -2,6 +2,7 @@ import numpy as np
 import scipy.sparse
 import networkx as nx
 
+
 def coarsen(A, levels, self_connections=False):
     """
     Coarsen a graph, represented by its adjacency matrix A, at multiple

### 2017-09-06 Work_report/Daily_progress/work_progress_daily.tex
Commit from the new computer Hue hue

@@
 \subsubsection{July 29 : Saturday}
+Probably no work done
+
+\section{Week}
+\subsection{Sept 6 : Thursday}
+Discussion with the prof. Main points noted below. Also has what all needs to be done before tomorrow's meeting.
+\begin{itemize}
+\item Graph Signal. Needs a more concrete definition. Can the vectors be of different dimensions? (I think not, but need to verify this.)
+\item An image may have 100-200 superpixels, which is not a constant.
+So can't use the same graph for all of them.
+Can we exploit the graph structure?
+GCN though requires the same graph structure to be followed, otherwise it won't be able to exploit the weights and would essentially require new training and generally useless.
+\item We would also like to encode the spatial connections of the superpixels.
+\item When we have arbitrary shape, we don't want to have any kind of orientation information, may mess things up.
+\end{itemize}
 
@@
 
-\end{document}
+\end{document}\grid

### 2017-09-06 Work_report/Daily_progress/work_progress_daily.tex
Adding in the minutes of the discussion today with professor

@@
 
-\section{Week}
+\section{Week 1 : September}
 \subsection{Sept 6 : Thursday}
@@
 \item When we have arbitrary shape, we don't want to have any kind of orientation information, may mess things up.
+\item Each superpixel would give some form of a feature vector and we would like to use this feature vector as inputs to the GCN. But need to check if the GCN would actually be of any use?
+\item We want to use Graph structure to get some kind of context between the superpixels. So this would be a context sensitive classifier. Need to do extensive literature survey on this.
+\item For the case of Co-segmentation the problem is that can we even preserve the graph structure? The nodes? The adjacency graph / matrix. Need to think about these things more carefully.
+\item Co-segmentation in general may include both seen/unseen categorization as well.
+We might need to train on one set of classes and still get outputs on another unseen set of classes.
+Prof gave the same example as mine, 30C2 combinations, or possibly 25C2 and test on the rest 5C2.
+We can get the corresponding ground truths as well.
+\item Two aspects to the problem of Co-segmentation.
+Say G1 has m nodes, and G2 has n nodes.
+We would like to perform subgraph matching problem.
+What Avik has done is used a greedy algorithm which gives the results quite fast.
+But I don't think that would be enough actually.
+Prof suggested to use Graph Neural Networks to solve this problem.
+This is actually a combinatorial problem.
+We would like to learn to solve this combinatorial problem.
+\item In one case the problem is one-to-one, but here it is possible that it is many-to-many.
+Because one superpixel may match to two smaller super pixels from the other graph and vice-versa.
+Solution exists for the one-to-one problem.
+Sayan's talk tomorrow on the jigsaw puzzle thing is also one-to-one.
+May need to check the feasibility of such problems.
+\item Subgraph Matching Using Deep Learning.
+\item The other aspect is the features that are bein given as inputs.
+Currently it is hog and color features which are in some sense hand-crafted.
+But what we probably need is more general features.
+I am thinking in the direction of dilated convolution.
+May be that can help.
+[Need to read this one too.]
+\item In graphs, the sub-graph matching is NP-complete. To get the MCS : currently greedy algorithm being employed.
+\item Another thing to note is that currently we are doing only 0th order. We would like it to be of say some k-ordered, i.e. see till k-hops.
+\item So the problem now effectively becomes matching a group of nodes to a group of nodes.
+A problem that could arise is that number of nodes of the two matching things may not be exactly the same.
+What we can possibly do is to bring the number of nodes to be the same, by clustering some very similar nodes together.
 \end{itemize}

### 2017-09-07 Work_report/Daily_progress/work_progress_daily.tex
Adding in the minutes of discussion with professor.
Next meet would be post midsem

@@
 \section{Week 1 : September}
-\subsection{Sept 6 : Thursday}
+\subsection{Sept 6 : Wednesday}
 Discussion with the prof. Main points noted below. Also has what all needs to be done before tomorrow's meeting.
@@
 
+\subsection{Sept 7 : Thursday}
+Minutes of the discussion with professor and my answers to the doubts we previously had.
+\begin{itemize}
+\item First if the graph structure is approximately the same, we can simply do an adjacency approximation and say that the learned parameters are shared across the graphs.
+\item Second if the dimensionality of the vectors in each node is different can go to some fixed length representation using attention mechanism.
+\item Third is that if the graph is completely different then we can pass on the laplacian as well.
+My suggestion and partly intuition is that given a graph signal $x_{G1}$ and graph signal $x_{G2}$ belonging to two different graphs, we should be able to find some kind of conversion using the attention mechanism previously described.
+\item Then we go to Sayan's Jigsaw puzzle. The problem is formulated in RNN way with LSTM cells.
+\item Need to understand how to apply the graph networks to the subgraph matching problems clearly.
+\item Also need to understand seq2seq models. One thing I need to know is to how do we manage the problem of having different length vectors in the seq2seq models.
+\item Need to read about : Graph Neural Networks as to how they are different from graph convolution networks in what way and all.
+Second is to read the gated graph attention mechanism given for alleviating different graph structure problem.
+\end{itemize}
+
 \bibliography{./papers.bib}

### 2017-09-08 Work_report/Daily_progress/work_progress_daily.tex
Extremely minor updates

@@
 Second is to read the gated graph attention mechanism given for alleviating different graph structure problem.
+\item Also understood basics of seq2seq model and what attention really is.
+Just a high level understanding though complete understanding would take a bit more time.
+Include in basics of beam search algorithm and some ways of doing more seq2seq for not fixed vector lengths.
+\end{itemize}
+
+\subsection{Sept 8 : Friday}
+\begin{itemize}
+\item Started reading about Graph Neural Networks.
 \end{itemize}

### 2017-09-08 code/graph_cnn/cnn_classes.py

@@ -22,6 +22,6 @@ class gcn_layer(object):
         # Coarsen a graph multiple times using the Metis algorithm
         # levels is the number of coarsened graphs
         self.coarse_graphs.append(G)
-
+        rid = np
         for i in range(levels):
             # Need to choose the weights for pairing

### 2017-09-18 code/graph_cnn/cnn_classes.py
Minor code progress

@@ -1,6 +1,6 @@
 # import torch
 import numpy as np
-import sklearn
+# import sklearn
 import networkx as nx
 
 
@@ -15,13 +15,15 @@ class gcn_layer(object):
         self.sparse_adj_mat = self.G.adjacency_matrix()
         self.coarse_graphs = list()
 
-    def coarsen(self):
-        # Coarsen a graph
+    # def metis(self, levels):
+    #     # Coarsen a graph multiple times using the Metis algorithm
+    #     # levels is the number of coarsened graphs
+    #     self.coarse_graphs.append(G)
+    #     # rid = np
+    #     for i in range(levels):
+    # Need to choose the weights for pairing
 
-    def metis(self, levels):
-        # Coarsen a graph multiple times using the Metis algorithm
-        # levels is the number of coarsened graphs
-        self.coarse_graphs.append(G)
-        rid = np
-        for i in range(levels):
-            # Need to choose the weights for pairing
+    # def coarsen(self):
+    # Coarsen a graph
+
+    # def metis_one_level(self, ):

### 2017-09-19 code/graph_cnn/cnn_classes.py
Partial progress to cnn_classes

@@ -2,28 +2,39 @@
 import numpy as np
 # import sklearn
 import networkx as nx
-
+import pdb
 
 class gcn_layer(object):
-    def __init__(self, adj_graph, is_sparse=False):
+    # def __init__(self, adj_graph, is_sparse=False):
+    def __init__(self, _G):
         # for the time being assuming that
         # one graph is enough to represent one layer
-        if is_sparse:
-            self.G = nx.from_scipy_sparse_matrix(adj_graph)
-        else:
-            self.G = nx.from_numpy_matrix(adj_graph)
-        self.sparse_adj_mat = self.G.adjacency_matrix()
+        # if is_sparse:
+        # self.G = nx.from_scipy_sparse_matrix(adj_graph)
+        # else:
+        # self.G = nx.from_numpy_matrix(adj_graph)
+        self.G = _G
+        # self.sparse_adj_mat = self.G.adjacency_matrix()
         self.coarse_graphs = list()
+        self.coarse_graphs.append(self.G)
 
-    # def metis(self, levels):
-    #     # Coarsen a graph multiple times using the Metis algorithm
-    #     # levels is the number of coarsened graphs
-    #     self.coarse_graphs.append(G)
-    #     # rid = np
-    #     for i in range(levels):
-    # Need to choose the weights for pairing
+    def one_level(self, graph_ind):
+        # G is a networkx graph
+        G = self.coarse_graphs[graph_ind]
+        adj_mat = nx.adjacency_matrix(G)
+        adj_mat_coo = adj_mat.tocoo()
+        degree_vec = adj_mat_coo.sum(axis=0)
+        rr, cc, vv = adj_mat_coo.row, adj_mat_coo.col, adj_mat_coo.data
+        pdb.set_trace()
+        marked_ind = np.zeros(rr.shape[0])
+        for i in range(rr.shape[0]):
+            if not marked_ind[i]:
+                marked_ind[i] = True
+                grac_max = -np.inf
+                # for j in
 
-    # def coarsen(self):
-    # Coarsen a graph
 
-    # def metis_one_level(self, ):
+if __name__ == '__main__':
+    grid_graph = nx.grid_graph(dim=[28, 28])
+    glayer = gcn_layer(grid_graph)
+    glayer.one_level(0)

### 2017-09-19 code/graph_cnn/cnn_classes.py
More or less coarsening done, but leaving it as is

@@ -1,8 +1,11 @@
+from __future__ import print_function
+from __future__ import division
 # import torch
 import numpy as np
 # import sklearn
 import networkx as nx
 import pdb
+
 
 class gcn_layer(object):
     # def __init__(self, adj_graph, is_sparse=False):
@@ -18,6 +21,11 @@ class gcn_layer(object):
         self.coarse_graphs = list()
         self.coarse_graphs.append(self.G)
 
+    def metis_all_levels(self, levels):
+        for i in range(levels):
+            G1 = self.one_level(-1)
+            self.coarse_graphs.append(G1)
+
     def one_level(self, graph_ind):
         # G is a networkx graph
         G = self.coarse_graphs[graph_ind]
@@ -25,13 +33,35 @@ class gcn_layer(object):
         adj_mat_coo = adj_mat.tocoo()
         degree_vec = adj_mat_coo.sum(axis=0)
         rr, cc, vv = adj_mat_coo.row, adj_mat_coo.col, adj_mat_coo.data
-        pdb.set_trace()
-        marked_ind = np.zeros(rr.shape[0])
-        for i in range(rr.shape[0]):
+        num_nodes = G.number_of_nodes()
+        # pdb.set_trace()
+        marked_ind = np.zeros(num_nodes)
+        cluster_arr = np.zeros(num_nodes)
+        c = 0
+        for i in range(num_nodes):
             if not marked_ind[i]:
                 marked_ind[i] = True
                 grac_max = -np.inf
-                # for j in
+                best_neighbor = -1
+                for j in G.neighbors(i):
+                    if not marked_ind[j]:
+                        wij = G[i][j]['weight']
+                        grac_tmp = wij * (1/degree_vec[i] + 1/degree_vec[j])
+                        if grac_tmp > grac_max:
+                            best_neighbor = j
+                            grac_max = grac_tmp
+
+                cluster_arr[i] = c
+                if best_neighbor > -1:
+                    marked_ind[best_neighbor] = True
+                    cluster_arr[best_neighbor] = c
+            c += 1
+        nrr, ncc, nvv = cluster_arr[rr], cluster_arr[cc], vv
+        N1 = cluster_arr.max() + 1
+        adj_mat_new = scipy.sparse.csr_matrix(nvv, (nrr, ncc), shape=(N1, N1))
+        adj_mat_new.eliminate_zeros()
+        G_new = nx.from_scipy_sparse_matrix(adj_mat_new)
+        return G_new
 
 
 if __name__ == '__main__':

### 2017-09-19 code/graph_cnn/lib/coarsening.py

@@ -1,7 +1,6 @@
 import numpy as np
 import scipy.sparse
-import networkx as nx
-
+import pdb
 
 def coarsen(A, levels, self_connections=False):
     """
@@ -9,7 +8,6 @@ def coarsen(A, levels, self_connections=False):
     levels.
     """
     graphs, parents = metis(A, levels)
-    graphs_new = []
     perms = compute_perm(parents)
 
     for i, A in enumerate(graphs):
@@ -25,13 +23,12 @@ def coarsen(A, levels, self_connections=False):
         A = A.tocsr()
         A.eliminate_zeros()
         graphs[i] = A
-        graphs_new.append(nx.from_numpy_matrix(A.todense()))
-        # G = nx.from_numpy_matrix(A.todense())
+
         Mnew, Mnew = A.shape
         print('Layer {0}: M_{0} = |V| = {1} nodes ({2} added),'
               '|E| = {3} edges'.format(i, Mnew, Mnew-M, A.nnz//2))
 
-    return graphs_new, perms[0] if levels > 0 else None
+    return graphs, perms[0] if levels > 0 else None
 
 
 def metis(W, levels, rid=None):
@@ -53,6 +50,7 @@ def metis(W, levels, rid=None):
     NOTE
     if "graph" is a list of length k, then "parents" will be a list of length k-1
     """
+
     N, N = W.shape
     if rid is None:
         rid = np.random.permutation(range(N))
@@ -95,8 +93,8 @@ def metis(W, levels, rid=None):
         nrr = cluster_id[rr]
         ncc = cluster_id[cc]
         nvv = vv
-        pdb.set_trace()
         Nnew = cluster_id.max() + 1
+        # pdb.set_trace()
         # CSR is more appropriate: row,val pairs appear multiple times
         W = scipy.sparse.csr_matrix((nvv,(nrr,ncc)), shape=(Nnew,Nnew))
         W.eliminate_zeros()
@@ -119,8 +117,7 @@ def metis(W, levels, rid=None):
 
 
 # Coarsen a graph given by rr,cc,vv.  rr is assumed to be ordered
-def metis_one_level(rr,cc,vv,rid,weights):
-
+def metis_one_level(rr, cc, vv, rid, weights):
     nnz = rr.shape[0]
     N = rr[nnz-1] + 1
 
@@ -241,6 +238,7 @@ def perm_data(x, indices):
         else:
             xnew[:,i] = np.zeros(N)
     return xnew
+
 
 def perm_adjacency(A, indices):
     """

### 2017-09-19 code/graph_cnn/lib/utils.py

@@ -1,0 +1,333 @@
+import gensim
+import sklearn, sklearn.datasets
+import sklearn.naive_bayes, sklearn.linear_model, sklearn.svm, sklearn.neighbors, sklearn.ensemble
+import matplotlib.pyplot as plt
+import scipy.sparse
+import numpy as np
+import time, re
+
+
+# Helpers to process text documents.
+
+
+class TextDataset(object):
+    def clean_text(self, num='substitute'):
+        # TODO: stemming, lemmatisation
+        for i,doc in enumerate(self.documents):
+            # Digits.
+            if num is 'spell':
+                doc = doc.replace('0', ' zero ')
+                doc = doc.replace('1', ' one ')
+                doc = doc.replace('2', ' two ')
+                doc = doc.replace('3', ' three ')
+                doc = doc.replace('4', ' four ')
+                doc = doc.replace('5', ' five ')
+                doc = doc.replace('6', ' six ')
+                doc = doc.replace('7', ' seven ')
+                doc = doc.replace('8', ' eight ')
+                doc = doc.replace('9', ' nine ')
+            elif num is 'substitute':
+                # All numbers are equal. Useful for embedding (countable words) ?
+                doc = re.sub('(\\d+)', ' NUM ', doc)
+            elif num is 'remove':
+                # Numbers are uninformative (they are all over the place). Useful for bag-of-words ?
+                # But maybe some kind of documents contain more numbers, e.g. finance.
+                # Some documents are indeed full of numbers. At least in 20NEWS.
+                doc = re.sub('[0-9]', ' ', doc)
+            # Remove everything except a-z characters and single space.
+            doc = doc.replace('$', ' dollar ')
+            doc = doc.lower()
+            doc = re.sub('[^a-z]', ' ', doc)
+            doc = ' '.join(doc.split())  # same as doc = re.sub('\s{2,}', ' ', doc)
+            self.documents[i] = doc
+
+    def vectorize(self, **params):
+        # TODO: count or tf-idf. Or in normalize ?
+        vectorizer = sklearn.feature_extraction.text.CountVectorizer(**params)
+        self.data = vectorizer.fit_transform(self.documents)
+        self.vocab = vectorizer.get_feature_names()
+        assert len(self.vocab) == self.data.shape[1]
+
+    def data_info(self, show_classes=False):
+        N, M = self.data.shape
+        sparsity = self.data.nnz / N / M * 100
[…]

### 2017-09-19 Work_report/Presentation/ECG/ecg_survey.tex
Updates to reference files for ecg

\documentclass{article}
\usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}

% \usepackage{siunitx}
% \sisetup{round-mode=places,round-precision=2}

\newcommand{\ra}{$\rightarrow$}

\title{Paper Summaries}
\author{
  Arka Sadhu}
\date{\today}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{QRS Analysis Algos}
\subsection{Signal Derivatives and Digital Filters}
\begin{itemize}
\item Typical f components in the range of 10-25 Hz, so most algos use a filter bank to attenuate other signal artifacts from P,T waves, baseline drift, incoupling noise.
\item For P,T waves use high pass filtering, for incoupling noise actually need a low pass filter, giving a bandpass filter from 10-25 Hz.
\item Some do it separately , some only take the high pass part of it.
\item Most algos use some kind of decision rules to reduce the number of false positives.
\end{itemize}
\subsubsection{Derivative Based Algos}
\begin{itemize}
\item HPF realized as a differentiator. Mostly first order, some also second order. Some cases a linear combination as well.
\item Detection by comparing the feature against a threshold.
\item Also complemented by heuristically found features
\end{itemize}
\subsubsection{Digital Filters}
\begin{itemize}
\item Two different lpf with different cut-off freq, subtraction gives bpf.
\item Passed onto simple m+-time step averaging.
\item MOBD (multiplicatio of backward difference) : kind of AND all algorithm  and some consistency conditions.
\item Simple peak detection search by comparing the max and following till v/2 of the signal. Mark the highest peak.
\item Do a form of lc of peak level and simple noise level and update, eventually threshold reached.
\item Another method : max of each segment compared to an adaptive noise level and adaptive peak estimate and classified depending on distance to each other.
\item Generalized digital filters also proposed.
\end{itemize}

\subsection{Wavelet, Singularity, Filter Bank}
\begin{itemize}
\item Use wavelet transform, in some sense similar to stft. Use discrete wavelet transform.
\item 32 band filter bank used to downsample subband signals.
\end{itemize}

\subsection{Neural Network Based Methods}

\end{document}

### 2017-09-19 Work_report/Presentation/ECG/ecg_survey.tex
Done for the day

@@
 
-\title{Paper Summaries}
+\title{ECG Analysis Summaries}
 \author{
@@
 \subsection{Neural Network Based Methods}
-
+\subsubsection{Neural Networks}
+\begin{itemize}
+\item ANN for non-linear signal processing. Mostly MLP, RBF, LVQ used. RBF closely related to fuzzy logic methods.
+\item LVQ has input layer, competitive layer, linear layer, competitive automatically learns to classify input vectors into subclasses where max subclasses is number of neurons.
+\item MLP, RBF trained using supervised, LVQ trained in an unsupervised manner.
+\end{itemize}
+\subsubsection{Neural Networks as Adaptive Non-linear Predictors}
+\begin{itemize}
+\item Since ecg contains mostly non-QRS segments, nn converges to a point where samples from non-QRS segments are well predicted, and segments with sudden changes (QRS segments) follow a different statistics and lead to sudden increase in the prediction error, which in itself can be used as a feature signal for QRS detection.
+\item Non-linear prediction using mlp, trained online and output is further passed through matched filter.
+\end{itemize}
+\subsubsection{LVQ for QRS-detection}
+\begin{itemize}
+\item Train a discrimination between QRS and PVC contractions.
+\item Not very good results, but once trained offers fast computations.
+\end{itemize}
+\subsection{Additional Approaches}
+\subsubsection{Adaptive Filters}
+\begin{itemize}
+\item Simple prediction filter to learn the weights using least mean square error.
+\end{itemize}
+\subsubsection{Hidden Markov Models}
+\begin{itemize}
+\item Possible states are P-wave, QRS, T-wave. Whole state sequence is inferred at once.
+\item Disadvantage is large computation complexity.
+\end{itemize}
+\subsubsection{Mathematical Morphology}
+\begin{itemize}
+\item Use of erosion and dilation.
+\item This gives a feature signal and QRS again got using thresholding.
+\end{itemize}
+\subsubsection{Matched Filter}
+\begin{itemize}
+\item Improves SNR.
+\item AMCD : Average magnitude cross difference method : computationally inexpensive alternative.
+\end{itemize}
+\subsubsection{Genetic Algorithms}
+\begin{itemize}
+\item Genetic algorithms applied to combined design of optimal polynomial filters for the pre-processing and decision stage.
+\item Decision stage mainly adaptive threshold, and optimized in conjunction with polynomial filters.
+\end{itemize}
+\subsubsection{Hilbert Transformed Based QRS-detection}
+\begin{itemize}
+\item Hilbert transform of the signal is used to compute the signal envelope.
+\item LPF to avoid ambiguity of peak detection.
+\end{itemize}
+\subsubsection{Length and Energy Transforms}
+\begin{itemize}
+\item Both assume that ecg is a vector.
+\item Length and energy transform are better features than conventional transforms of feature extractions.
+\end{itemize}
+\subsubsection{Synctactic Methods}
+\begin{itemize}
+\item Signal assumed to be concatenation of linguistically represented primary patterns i.e. strings. Use grammar to search for code strings.
+\item Due to computational efficiency mostly use line segments as primitives for the signal representation.
+\end{itemize}
+\subsubsection{QRS Detection Based on MAP estimate}
+\begin{itemize}
+\item Prior of linear combination of pulse-shaped peaks.
+\end{itemize}
+\subsubsection{Zero-crossing based QRS Detection}
+\begin{itemize}
+\item After bpf a high freq sequence is added. Non-QRS segment has more zero crossing than QRS segment.
+\end{itemize}
+\subsection{Benchmark Databases}
+\subsubsection{MIT-BIH Database}
+\begin{itemize}
+\item Ten databases for various test purposes.
+\item Most frequently MIT-BIH Arrythmia database is used.
+Contains 48 half hour recordings of annotated ECG with sampling rate of 360Hz and 11bit resolution over 10mV range.
+For some cases detection is quite difficult because of abnormal shapes, noise and artifacts.
+\end{itemize}
+\subsubsection{AHA Databse}
+\begin{itemize}
+\item 155 recordings of ambulatory ECG for Ventricular Arrythmia Detectors.
+\end{itemize}
+\subsubsection{Ann Arbor Electrogram Libraries}
+\begin{itemize}
+\item Not relevant.
+\end{itemize}
+\subsubsection{CSE Database}
+\begin{itemize}
+\item Contains 1000 multi-lead recordings (12-15 leads).
+\end{itemize}
+\subsubsection{Other standard Databases}
+\begin{itemize}
+\item European ST-T
+\item QT
+\item MGH
+\item IMPROVE
+\item PTB
+\end{itemize}
 \end{document}

### 2017-09-22 code/cnn_ecg/ecg_cnn.py
Started ecg code a bit

@@ -1,0 +1,11 @@
+import os
+import wfdb
+
+class ecg_one_data_holder():
+    def __init__(self, tdir):
+        self.sig, self.fields = wfdb.rdsamp(tdir)
+
+# class ecg_all_data_holder():
+#     def __init__(self, tdir, control_list):
+#         self.tdir = tdir
+        

### 2017-10-17 code/cnn_ecg/ecg_cnn.py
Adding deformable conv presentation half done

@@ -4,29 +4,40 @@ import time
 # import pickle
 import torch
 from torch.autograd import Variable
+from torch.utils.data import Dataset
+
+# class ecg_one_data_holder():
+#     def __init__(self, tfile):
+#         self.tfile = tfile
+#         # pdb.set_trace()
+#         self.sig, self.fields = wfdb.srdsamp(tfile)
+#         # self.fields = fields['comments'][4]
+#         return
 
 
-class ecg_one_data_holder():
-    def __init__(self, tfile):
-        self.tfile = tfile
-        # pdb.set_trace()
-        self.sig, self.fields = wfdb.srdsamp(tfile)
-        # self.fields = fields['comments'][4]
-        return
+# class ecg_all_data_holder():
+#     def __init__(self, tdir, patient_list):
+#         self.tdir = tdir
+#         self.patient_list = patient_list
+#         self.ecg_data = list()
+#         return
 
+#     def populate_data(self):
+#         for ind, f in enumerate(self.patient_list):
+#             one_ecg_info = ecg_one_data_holder(self.tdir + f)
+#             self.ecg_data.append(one_ecg_info)
+#         return
 
-class ecg_all_data_holder():
+class ecg_dataset(Dataset):
     def __init__(self, tdir, patient_list):
         self.tdir = tdir
         self.patient_list = patient_list
-        self.ecg_data = list()
-        return
 
-    def populate_data(self):
-        for ind, f in enumerate(self.patient_list):
-            one_ecg_info = ecg_one_data_holder(self.tdir + f)
-            self.ecg_data.append(one_ecg_info)
-        return
+    def __len__(self):
+        return len(self.patient_list)
+
+    def __getitem__(self, idx):
+        sig, fields = wfdb.srdsamp(self.tdir + self.patient_list[idx])
 
 
 if __name__ == '__main__':

### 2017-11-22 Work_report/Final_presentation/btp_presentation.tex
Adding final presentation

\documentclass{beamer}
\usetheme{Boadilla}
% \usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{multirow}
% \mode<presentation>{
%     \AtBeginSection[]
%     {
%     \begin{frame}[allowframebreaks]{Outline}
%     \tableofcontents[currentsection]
%     \end{frame}
%     }
% }
% \AtBeginSubsection[
%   {\frame<beamer>{\frametitle{Outline}
%     \tableofcontents[currentsection,currentsubsection]}}%
% ]%
% {
%   \frame<beamer>{
%     \frametitle{Outline}
%     \tableofcontents[currentsection,currentsubsection]}
% }

\title{ECG Disease Classification Using Graph Convolution Networks}
% \subtitle{Using Beamer}
\author{Arka Sadhu}
\institute{IIT Bombay}
\date{\today}

\begin{document}
% document goes here

\begin{frame}
\titlepage
\end{frame}

% \begin{frame}
% \frametitle{Outline}
% \tableofcontents
% \end{frame}

\section{Problem Statement and Motivation}

% \subsection{Why GCN}
\begin{frame}
  \frametitle{Problem Statement}
  \begin{itemize}
  \item We are given annotated ECG data, i.e. ECG recordings along with the corresponding disease.
  \item Given a new ECG sample, we want to clasify into the different categories of disease.
  \item In current framework, only considered one-label classification, not multi-labeling.
  \item Previous work can be classified into two categories:
    \begin{itemize}
    \item Signal Processing techniques for good feature extraction (eg. QRS peak detection) coupled with standard Machine Learning approaches.
    \item Neural Networks for extraction of feature as well as for classification (eg. Convolutional Networks as there is periodicity associated)
    \end{itemize}
  \item We want to extend the success of Neural Networks to this task as well.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Heart diseases considered}
  The following heart diseases are considered:
  \begin{itemize}
  \item Myocardial Infarction
  \item Cardiomyopathy \ Heart failure
  \item Bundle branch block
  \item Dysrhythmia
  \item Myocarditis
  \end{itemize}
\end{frame}

\section{CNN on ECG}
\begin{frame}
  \frametitle{Dataset}
  The dataset used for experiments is the PTB databas from Physionet repository.
  \begin{itemize}
  \item Consists of 15 channels (12 for conventional ecgs, 3 frank leads).
  \item Resolution is 16bit and sampling rate is 1kHz.
  \item Total 549 recordings from 290 subjects. 148 are diagnosed with Myocardial Infarction (MI).
  \item We use parts of each classification for training and rest for testing.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{CNN on ECG}
  A simple Convolutional Network is tested on ECG.
  \begin{itemize}
  \item Architecture adopted is 1D version of the LeNet architecture. The network is :
    $$conv -> max pool -> conv -> max pool -> fc -> fc -> softmax$$
  \item Base implementation results in accuracy around 80-87\%.
  \item On top of each convolution layer, we add a batch normalization.
  \item This gives accuracy boost upto 93\%-94\%
  \item State of the Art to the best of knowledge is 96\%
  \item It is also noted that using more number of channels doesn't lead to increase in the accuracy.
  \end{itemize}
\end{frame}

\section{Graph CNN}
\begin{frame}
  \frametitle{Exploiting Data from Different Channels}
  \begin{itemize}
  \item We note that the ECG leads are put at particular locations. We would like to be able to use the underlying spatial distribution as well and incorporate data from the different leads. This is something that the standard CNN can not do.
  \item For this reason we go to Graph Convolutional Networks. This can be viewed as a generalization of CNN to non-euclidean spaces.
  \item It is not trivial to generalize CNN to non-euclidean spaces.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Graph CNN (Optional)}
  Two main approaches to Graph CNN
  \begin{itemize}
  \item Spectral Approach [ChebNet, NIPS2016]
  \item Spatial Approach [MoNet, CVPR2017]
  \end{itemize}
  A limitation of Spectral Approach is that the underlying graph should be fixed, which is precisely the case for ECG.
\end{frame}
% \subsection{How to extend convolution to graphs?}
% \begin{frame}
%   \frametitle{Extending Convolutional to Graphs}
%   There are two main approaches
%   \begin{itemize}
%   \item <1->Spatial Approach :\\
%     Generalization of CNN in the spatial domain itself.
%     \begin{itemize}
%     \item <1-> Learning Convolutional Neural Networks for Graphs [ICML 2016].% \cite{DBLP:journals/corr/NiepertAK16}
%     \end{itemize}
%   \item <2-> Spectral Approach :\\
%     Using the frequency characterization of CNN and using that to generalize to Graphical domain
%     \begin{itemize}
%     \item <2->Spectral Networks and Deep Locally Connected Networks on Graphs [Bruna et al. ICLR 2014]. % \cite{DBLP:journals/corr/BrunaZSL13} %
%     \item <2->Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering [Defferrard et al. NIPS 2016] (will be the main focus) % \cite{DBLP:journals/corr/DefferrardBV16}
%     \item <2->Semi-Supervised Classification with Graph Convolutional Networks [Kipf et al. ICLR 2017] % \cite{DBLP:journals/corr/KipfW16}
%     \end{itemize}
%   \end{itemize}
% \end{frame}

% \section{Problems with Spatial Approach}
% \begin{frame}
%   \frametitle{Limitations of Spatial Approach}
%   \begin{itemize}
%   \item Can't exactly define a neighborhood because the distances are not uniform.
%   \item Ordering of nodes is problem specific.
%   \end{itemize}
%   Hence for the remainder we discuss the Spectral Approach
% \end{frame}

% \section{Spectral Approach}
% % \subsection{Basics of Spectral Approach}
% \begin{frame}
%   \frametitle{A Basic Formulation}
%   \begin{itemize}
%   \item Convolution in spectral (Fourier) domain is point wise multiplication.
%   \item Fourier Basis is defined as the eigen basis of the laplacian operator.
%   \item Can use Laplacian of a graph.
%   \end{itemize}
% \end{frame}

% % \subsection{Problem Formulation}
% \begin{frame}
%   \frametitle{Defining the Problem on Graphs}
%   \begin{itemize}
%   \item A feature description $x_i$ for every node $i$; summarized in a $N x D$ feature matrix $X$ ($N$ : number of nodes, $D$ : number of input features)
%   \item Adjacency Matrix $A$.
%   \item  Node level output $Z$ (an $N x F$ feature matrix, where $F$ = number of output features per node).
%   \item  Every neural network can then be written as a non-linear function.
%     $$H^{(l+1)} = f(H^{l}, A)$$
%   \end{itemize}
% \end{frame}

% % \subsection{Graph Laplacian}
% \begin{frame}
%   \frametitle{Brief overview of Graph Laplacian}
%   Let $T$ denote the diagonal matrix with ($v$,$v$)-th entry having value $d_v$ : degree of vertex $v$.
%   % $$L(u,v) = $$
%   Define L-matrix as
%   \[
%     L(u,v) =
%     \begin{cases}
%       d_v &\quad\text{if u = v}\\
%       -1 &\quad\text{if u and v are adjacent}\\
%       0 &\quad \text{otherwise}\\
%     \end{cases}
%   \]
%   And the Laplacian of the graph as
%   \[
%     \mathcal{L}(u,v) =
%     \begin{cases}
%       1 &\quad\text{if u = v}\\
%       -\frac{1}{\sqrt{d_ud_v}} &\quad\text{if u and v are adjacent}\\
%       0 &\quad \text{otherwise}\\
%     \end{cases}
%   \]
% \end{frame}

% \begin{frame}
%   \frametitle{Graph Laplacian (contd.)}
%   $$\mathcal{L} = T^{-1/2}LT^{1/2}$$
%   With the convention $T^{-1}(v,v) = 0$ for $d_v = 0$.\\
%   When G is k-regular,
%   $$\mathcal{L} = I - \frac{1}{k}A$$
%   For a general graph
%   $$\mathcal{L} = I - T^{-1/2}AT^{1/2}$$
% \end{frame}
% \section{Spectral Networks and Deep Locally Connected Networks on Graphs}
% \begin{frame}
%   \frametitle{Spectral Networks and Deep Locally Connected Networks on Graphs}
%   \begin{itemize}
%   \item Mentions the use of both spatial and spectral construction.
%   \item For the spectral part uses a spline and has k control points for it.
%     $$g_{\theta}(\Lambda) = B\theta$$
%     Here $B$ is the cubic B-spline basis and $\theta$ is a vector of control points.
%   \item The datasets used (created) are quite interesting. Subsampled MNIST and MNIST on sphere to show how spectral networks can be used on graphs.
%   \end{itemize}
% \end{frame}

% \section{CNN on Graphs with Fast Localized Spectral Filtering}
% \subsection{Learning fast localized Spectral filters}
% \begin{frame}
%   \frametitle{Graph Fourier Transform}
%   \begin{itemize}
%   \item Laplcian of the graph is real symmetric positive semidefinite, and thus can be written as
%     $$L = U \Lambda U^{T}$$
%   \item Here $U = [u_0 .... u_{n-1}]$ is the fourier basis and $\Lambda = diag([\lambda_0...\lambda_{n-1}])$ are ordered real non-negative eigen values.
%   \item Graph Fourier Transform of a signal $x$ is $\hat{x} = U^{T}x$.
%   \end{itemize}
% \end{frame}

% \begin{frame}
%   \frametitle{Spectral filtering of graph signals}
%   \begin{itemize}
%   \item Defining convolution on graphs
%     $$ x *_{G} y = U((U^T x) \odot (U^T y))$$
%   \item Filtering by $g_{\theta}$
%     $$ y = g_{\theta}(L)x = g_{\theta}(U \Lambda U^{T})x = Ug_{\theta}(\Lambda) U^T x $$
%   \item A non-parametric filter (all parameters free) would be defined as
%     $$g_{\theta}(\Lambda) = diag(\theta)$$
%   \end{itemize}
% \end{frame}

% \begin{frame}
%   \frametitle{Polynomial Parametrization}
%   \begin{itemize}
%   \item   Problem with non-parametric filters is that not localized (we want something like k-neighborhood) and therefore their learning complexity becomes $O(n)$. This can be overcomed with use of a Polynomial filter
%     $$g_{\theta}(\Lambda) = \sum_{k = 0}^{K-1}\theta_k\Lambda^k$$
%   \item The advantage we gain here is that nodes which are at a distance greater than $K$ away from the node $i$, at which the filter is applied, are not affected. Hence we have gained localization.
%   \end{itemize}
% \end{frame}

% \begin{frame}
%   \frametitle{Recursive formulation for fast filtering}
%   \begin{itemize}
%   \item Still cost to filter is high $O(n^2)$ because of multiplication with $U$ matrix.
%   \item Therefore use recurrence relation of chebyshev polynomial instead.
%     $$g_{\theta}(\Lambda) = \sum_{k=0}^{K-1}\theta_k T_K(\tilde{\Lambda})$$
%     Here $\tilde{\Lambda}$ is scaled between $[-1,1]$.
%   \item This allows us to compute $\bar{x_k} = T_K{\tilde{L}}x$. And Therefore
%     $$ y = g_{\theta}(L)x = [\bar{x_0}...\bar{x_{k-1}}]\theta$$
%   \item The cost is now $O(K|E|)$
%   \end{itemize}
% \end{frame}

% \begin{frame}
%   \frametitle{Learning filters}
%   \begin{itemize}
%   \item Trivial to show that backprop calculation can be done efficiently.
%   \end{itemize}
% \end{frame}

% \subsection{Coarsening and Pooling}
% \begin{frame}
%   \frametitle{Graph Coarsening and Pooling}
%   \begin{itemize}
%   \item Require efficient mechanism for pooling. Graph clustering as such is NP-hard and some approximations must be made.
%   \item The paper uses Graclus algorithm for coarsening, and uses an intelligent way of rearranging the nodes [creating a balanced binary tree from the remaining singleton and fake nodes] so that the pooling now becomes equivalent to pooling a regular 1D signal.
%   \end{itemize}
% \end{frame}

% \subsection{Results on MNIST}
% \begin{frame}
%   \frametitle{MNIST results}
%   \begin{itemize}
%   \item Achieves close to classical CNN accuracy.
%     % \item Pictures to be added.
%     \begin{table}[H]
%       \centering
%       \caption{MNIST performance}
%       \label{t:mn_perf}
%       \begin{tabular}{|l|l|l|l|l|l|l|l|}
%         \hline
%         \multicolumn{2}{|l|}{accuracy} & \multicolumn{2}{l|}{loss} & \multirow{2}{*}{name}       \\ \cline{1-4}
%         test           & train         & test        & train       &                             \\ \hline
%         98.87          & 99.62         & 1.02e+00    & 9.99e-01    & cgconv\_cgconv\_fc\_softmax \\ \hline
%         98.00          & 99.26         & 6.52e-02    & 2.77e-02    & cgconv\_softmax             \\ \hline
%         96.75          & 96.78         & 1.12e+00    & 1.12e+00    & fgconv\_fgconv\_fc\_softmax \\ \hline
%         95.91          & 95.50         & 1.44e-01    & 1.53e-01    & fgconv\_softmax             \\ \hline
%         97.66          & 97.79         & 1.09e+00    & 1.08e+00    & sgconv\_sgconv\_fc\_softmax \\ \hline
%         96.95          & 97.27         & 1.03e-01    & 9.46e-02    & sgconv\_softmax             \\ \hline
%         92.18          & 92.47         & 3.14e-01    & 3.14e-01    & softmax                     \\ \hline
%       \end{tabular}
%     \end{table}
% \end{itemize}
% \end{frame}

% \begin{frame}
%   \frametitle{Accuracy and Loss Plots}
%   \begin{figure}[H]
%     \centering
%     \includegraphics[scale=0.38]{images/accuracy_plot.png}
%     \caption{Accuracy and Loss function plot}
%     \label{fig:acl_mnist}
%   \end{figure}

% \end{frame}
% \section{Semi-Supervised Classification with Graph Convolutional Networks}
% \begin{frame}
%   \frametitle{Fast approximate convolutions on the graph}
%   \begin{itemize}
%   \item Layerwise propagation rule as
%     $$H^{(l+1)} = \sigma(\tilde{D}^{-1/2}\tilde{A}\tilde{D}^{-1/2}H^{(l)}W^{(l)})$$
%     Here $\tilde{A} = A + I_N$ the adjacency matrix with added self-loops. $\tilde{D}$ is the degree matrix.
%   \item In the chebyshev approximation, limit to $K=1$ and therefore the layer-wise convolution operation is linear function of the laplacian.
%   \item Experimentally shows 2-3 layered GCN can effectively learn standard graph problems. Specifically it does decently well in the unsupervised case, and significantly good in the semi-supervised setting.
%   \end{itemize}
% \end{frame}

% \section{Limitations of Graph Convolutional Networks}
% \begin{frame}
%   \frametitle{Limitations}
%   \begin{itemize}
%   \item We would like to model a network which doesn't require a rectangular input size and therefore be able to accomodate superpixels. In theory this should be possible, but there are a few points that we need to keep in mind.
%     \begin{itemize}
%     \item Graph doesn't have orientation. There is no sense of up, down, left or right. The filters are rotationally invariant. This can be both advantageous as well as disadvantageous depending on the set-up of the problem. Spatial Transformer Networks learn the invariance to rotation as well as generic warping. But there is always the problem of '6' and '9' because they are equivalent in modulo rotation.
%     \item The filters are not directly transferable to another graph (because of the graph laplacian).
%     \end{itemize}
%   \end{itemize}
% \end{frame}

% \bibliography{ref.bib}
% \bibliographystyle{ieeetr}

\end{document}

### 2017-11-22 Work_report/Final_presentation/btp_presentation.tex
More or less done

@@
 \begin{frame}
+  \frametitle{Motivation}
+  We wish to classify the disease of person based on raw ECG data.
+  \begin{itemize}
+  \item The main motivation comes from being able to capture real time ECG data and use that monitor the occurence of any heart related problem in the patient.
+  \item This can also serve as a second opinion to the doctor.
+  \end{itemize}
+  Problems with Existing Methods:
+  \begin{itemize}
+  \item Signal Processing Techniques often may be computationally expensive and cannot work in real time.
+  \item Need extremely high accuracy perhaps so as to not to trigger false alarms.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
   \frametitle{Heart diseases considered}
@@
   \end{itemize}
+  Currently, we are bothered only with Myocardial Infarction which is major part of the PTB dataset (described next).
+\end{frame}
+
+\begin{frame}
+  \frametitle{Methodology}
+  The following methodology is followed:
+  \begin{itemize}
+  \item First we analyze using simple Convolutional Neural Networks [CNN] for our problem.
+CNN are a good starting point as they are well known for their spatial invariance which in 1D can be considered as the temporal invariance which is something required in a continuous ECG data.
+  \item Next we hope to understand what things CNN is able to learn well and what it is not. In particular we want to identify some Ad-Hocs which lead to better convergence of the Neural Network.
+  \item Then we want to know the bottleneck of the learning and what we can do to improve it, which introduces us to Graph CNN.
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Dataset}
-  The dataset used for experiments is the PTB databas from Physionet repository.
+  The dataset used for experiments is the PTB database from Physionet repository.
   \begin{itemize}
@@
   \item Base implementation results in accuracy around 80-87\%.
-  \item On top of each convolution layer, we add a batch normalization.
-  \item This gives accuracy boost upto 93\%-94\%
-  \item State of the Art to the best of knowledge is 96\%
+  \item Some Ad-Hocs are required to get better results.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{CNN on ECG (contd.)}
+  \begin{itemize}
+  \item Since data is not so much, each ECG data is pre-processed by taking the samples upto fixed period only (eg. 38000 points are broken into 27 partitions).
+  \item On top of each convolution layer, we add a batch normalization. This gives accuracy boost upto 93\%-94\%
+  \item State of the Art to the best of my knowledge on the PTB dataset is 96\%.
   \item It is also noted that using more number of channels doesn't lead to increase in the accuracy.
   \end{itemize}
+  We would like to do better.
+\end{frame}
+
+\begin{frame}
+  \frametitle{Results on using CNNs on ECG}
+  \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.5]{images/bn_before_relu_acc_94_3}
+    \caption{Accuracy of validation set vs Number of epochs}
+    \label{fig:1}
+  \end{figure}
 \end{frame}
@@
   \item Spectral Approach [ChebNet, NIPS2016]
+    \begin{itemize}
+    \item Basic Idea : Use graph laplacian and do convolution operation in the spectral domain.
+    \end{itemize}
   \item Spatial Approach [MoNet, CVPR2017]
+    \begin{itemize}
+    \item Basic Idea : Use a local manifold and learn in polar coordinates.
     \end{itemize}
-  A limitation of Spectral Approach is that the underlying graph should be fixed, which is precisely the case for ECG.
+  \end{itemize}
+  A limitation of Spectral Approach is that the underlying graph should be fixed, which is fortunately the case for ECG.
 \end{frame}
+
+\begin{frame}
+  \frametitle{ChebNet (Optional)}
+  Main Ideas in ChebNet:
+  \begin{itemize}
+  \item Uses graph laplacian and computes convolution in the fourier domain (using graph fourier transform).
+  \item Restricts convolution to a local domain (k-hops) even when using the spectral approach.
+  \item Efficient computation of the graph convoluion using the Chebyshev Polynomials.
+  \item Efficient coarsening and pooling operation on graphs.
+  \end{itemize}
+  Main Limitation:
+  \begin{itemize}
+  \item The graph should be fixed. Cannot learn on multiple graphs.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{ChebNet on ECG data}
+  This is still Work In Progress. Code is ready and small bug fixes are to be made.
+  % \begin{itemize}
+  % \item Main limitation is that the code is
+  % \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Main Limitations of the Approach}
+  \begin{itemize}
+  \item Neural Networks are in general data hungry. We would need large amounts of data. Unfortunately, annotated Medical data is not very easily available.
+  \item Data is not directly interpretable and needs the eye of a professional. Makes debugging difficult.
+  \item In usual applications of graph convolution networks, the number of nodes can be quite high which allows for efficiently using pooling and convolutions.
+For a small network like ECG with only 12 nodes it remains to be seen how much improvement the Graph CNN will give over vanilla CNN.
+  \end{itemize}
+\end{frame}
+
+\section{Future Work}
+\begin{frame}
+  \frametitle{Future Work}
+  \begin{itemize}
+  \item Get the results on ECG data using ChebNet.
+  \item Extend the results to larger datasets and even Holter ECG data.
+  \item Extend the work on ECG data to EEG data as the problem space is extremely similar except for the added number of channels.
+  \end{itemize}
+\end{frame}
+
 % \subsection{How to extend convolution to graphs?}

### 2017-11-23 Work_report/Final_presentation/btp_presentation.tex
Adding btp

@@
 % \subtitle{Using Beamer}
-\author{Arka Sadhu}
+\author[Arka Sadhu]{Arka Sadhu \\ Supervised by Prof. Subhasis Chaudhuri}
 \institute{IIT Bombay}
@@
   \item On top of each convolution layer, we add a batch normalization. This gives accuracy boost upto 93\%-94\%
-  \item State of the Art to the best of my knowledge on the PTB dataset is 96\%.
+  \item State of the Art to the best of my knowledge on the PTB dataset is 96\% [1]
   \item It is also noted that using more number of channels doesn't lead to increase in the accuracy.
@@
   \begin{itemize}
-  \item Spectral Approach [ChebNet, NIPS2016]
+  \item Spectral Approach [ChebNet, NIPS2016][2]
     \begin{itemize}
@@
     \end{itemize}
-  \item Spatial Approach [MoNet, CVPR2017]
+  \item Spatial Approach [MoNet, CVPR2017][3]
     \begin{itemize}
@@
 
+\begin{frame}
+  \frametitle{References}
+  \begin{enumerate}
+  \item L.
+N.
+Sharma, R.
+K.
+Tripathy and S.
+Dandapat, "Multiscale Energy and Eigenspace Approach to Detection and Localization of Myocardial Infarction," IEEE Trans.
+Biomed.
+Eng.
+, vol.
+62, no.
+7, pp.
+1827-1837, Jul.
+2015
+  \item M. Defferrard, X. Bresson, P. Vandergheynst, Convolutional Neural Networks on Graphs with Fast Localized Spectral Filtering, NIPS 2016 (ChebNet framework)
+  \item F. Monti*, D. Boscaini*, J. Masci, E. Rodolà, J. Svoboda, M. M. Bronstein, Geometric deep learning on graphs and manifolds using mixture model CNNs, CVPR 2017 (MoNet framework)
+  \end{enumerate}
+
+\end{frame}
 % \subsection{How to extend convolution to graphs?}

### 2017-11-23 code/cnn_ecg/mimic_download.py

@@ -18,8 +18,8 @@ with open('/home/SharedData/Ark_git_files/mimic-code/mimic3_matcheddb/RECORDS-nu
 # Getting top 2000 person data
 n = 1000
 batch = 4
-record_wf_to_dl = record_waveforms[:n]
-record_n_to_dl = record_numerics[:n]
+record_wf_to_dl = record_waveforms[n:n+n]
+record_n_to_dl = record_numerics[n:n+n]
 db = 'mimic3wdb/matched'
 dl_dir = '/home/SharedData/Ark_git_files/mimic-code/mimic3_matcheddb/'
 numeric_problems = list()

### 2018-02-05 code/graph_cnn_ecg/ecg_cnn_graph_robust.py
Some decent progress, but decrease in accuracy

@@ -2,6 +2,7 @@ import wfdb
 import torch
 from torch.autograd import Variable
 # from torch.utils.data import Dataset, DataLoader
+from torch.utils.data import DataLoader
 from data_loader import ecg_dataset_simple
 from nn_model import simple_net
 from nn_trainer import simple_trainer
@@ -14,10 +15,11 @@ from cfg import all_vars
 
 if __name__ == "__main__":
     ptb_tdir = Path('/home/SharedData/Ark_git_files/btp_extra_files/ecg-analysis/')
+    ptb_tdir_str = str(ptb_tdir / 'data') + '/'
     # ptb_dat_dir = ptb_tdir / 'data'
-    patient_list_file = ptb_tdir / 'data' / 'patients.txt'
-    control_list_file = ptb_tdir / 'control.txt'
-    positive_list_file = ptb_tdir / 'positive.txt'
+    patient_list_file = str(ptb_tdir / 'data' / 'patients.txt')
+    control_list_file = str(ptb_tdir / 'control.txt')
+    positive_list_file = str(ptb_tdir / 'positive.txt')
 
     with open(patient_list_file, 'r') as f:
         patient_list = f.read().splitlines()
@@ -32,3 +34,27 @@ if __name__ == "__main__":
     batch_size = all_var['batch_size']
     num_tr_points = all_var['num_tr_points']
     channels = all_var['channels']
+
+    contr_tr_pts = int(num_tr_points*len(control_list)/len(patient_list))
+    post_tr_pts = int(num_tr_points*len(positive_list)/len(patient_list))
+    remain_tr_pts = num_tr_points - contr_tr_pts - post_tr_pts
+    remainder_list = list(set(patient_list) ^ set(control_list) ^ set(positive_list))
+
+    train_list = (control_list[:contr_tr_pts] + positive_list[:post_tr_pts] +
+                  remainder_list[:remain_tr_pts])
+    test_list = (control_list[contr_tr_pts:] + positive_list[post_tr_pts:] +
+                 remainder_list[remain_tr_pts:])
+
+    with torch.cuda.device(1):
+        ecg_train_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, train_list, Din, partitions=27,
+                                                         channels=channels),
+                                      batch_size=batch_size, shuffle=True, num_workers=2)
+        ecg_test_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, test_list, Din,
[…]

### 2018-02-05 code/graph_cnn_ecg/nn_trainer.py

@@ -1,6 +1,7 @@
 import torch
 from torch.autograd import Variable
 import matplotlib.pyplot as plt
+import numpy as np
 
 if torch.cuda.is_available():
     print('cuda available')
@@ -79,7 +80,7 @@ class ecg_trainer:
             print('  accuracy(test) = %.3f %%' % (running_accuray_test / running_total_test))
 
 
-class simple_trainer():
+class simple_trainer:
     def __init__(self, nn_model, train_loader=None, test_loader=None,
                  loss_fn=None, optimizer='adam'):
         self.nn_model = nn_model
@@ -106,6 +107,7 @@ class simple_trainer():
             line, = ax.plot(epoch_list, val_acc, 'ko-')
         for epoch in range(num_epoch):
             running_loss = 0
+            num_tr_iter = 0
             for ind, sample in enumerate(self.train_loader):
                 instance = Variable(sample['sig'].cuda())
                 label = Variable(sample['label'].cuda())
@@ -125,8 +127,8 @@ class simple_trainer():
                 # if ind % 100 == 0:
                 # if True:
                 # print(epoch, running_loss/num_tr_points)
-
-            print('epoch', epoch, running_loss/num_tr_points)
+                num_tr_iter += 1
+            print('epoch', epoch, running_loss/num_tr_iter)
             # pdb.set_trace()
             if plt_fig:
                 epoch_list = np.concatenate((line.get_xdata(), [epoch]))

### 2018-02-06 code/graph_cnn_ecg/cfg.py
Decent progress, hope to finish by tomorrow

@@ -1,6 +1,6 @@
 def all_vars():
     all_var = dict()
-    all_var['Din'] = 1000
+    all_var['Din'] = 750
     all_var['batch_size'] = 4
     all_var['num_tr_points'] = 300
     all_var['channels'] = [7]

### 2018-02-06 code/graph_cnn_ecg/ecg_cnn_graph_robust.py

@@ -12,6 +12,8 @@ import numpy as np
 # import pathlib
 from pathlib import Path
 from cfg import all_vars
+from lib.grid_graph import simple_graph
+
 
 if __name__ == "__main__":
     ptb_tdir = Path('/home/SharedData/Ark_git_files/btp_extra_files/ecg-analysis/')
@@ -45,9 +47,11 @@ if __name__ == "__main__":
     test_list = (control_list[contr_tr_pts:] + positive_list[post_tr_pts:] +
                  remainder_list[remain_tr_pts:])
 
+    small_graph = simple_graph()
+
     with torch.cuda.device(1):
-        ecg_train_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, train_list, Din, partitions=27,
-                                                         channels=channels),
+        ecg_train_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, train_list,
+                                                         Din, partitions=27, channels=channels),
                                       batch_size=batch_size, shuffle=True, num_workers=2)
         ecg_test_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, test_list, Din,
                                                         partitions=batch_size, channels=channels),

### 2018-02-06 code/graph_cnn_ecg/lib/grid_graph.py

@@ -5,7 +5,7 @@ import scipy.sparse, scipy.sparse.linalg  # scipy.spatial.distance
 import scipy.linalg
 import numpy as np
 import pdb
-
+import itertools
 
 def grid_graph(grid_side,number_edges,metric):
     """Generate graph of a grid"""
@@ -74,6 +74,21 @@ def path_graph(t_units=750, metric='euclidean'):
     p_graph = nx.path_graph(t_units)
     A = nx.adjacency_matrix(p_graph)
     print("nb edges: ", A.nnz)
+    return A
+
+
+def simple_graph(n=6, create_using=None, number_edges=2, metric='euclidean'):
+    z = np.empty((6, 2))
+    for ind, th in enumerate(np.arange(0, np.pi/1.9, np.pi/10)):
+        z[ind, 0] = np.cos(th)
+        z[ind, 1] = np.sin(th)
+    # return z
+    # z[0, 1] =
+    dist, idx = distance_sklearn_metrics(z, k=number_edges, metric=metric)
+    A = adjacency(dist, idx)
+    G = nx.from_scipy_sparse_matrix(A)
+    nx.draw(G)
+    print(A.data)
     return A
 
 

### 2018-02-06 code/graph_cnn_ecg/nn_model.py

@@ -475,10 +475,13 @@ class simple_net(torch.nn.Module):
 
     def forward(self, inp):
         # out = F.relu(F.max_pool1d(self.conv1_bn(self.conv1(inp)), 2))
+        layer_outs = dict()
         out = F.max_pool1d(self.conv1_bn(F.relu(self.conv1(inp))), 2)
         # out = F.dropout(out)
         # out = F.relu(F.max_pool1d(self.conv2_bn(self.conv2(out)), 2))
+        layer_outs['conv1'] = out
         out = F.max_pool1d(self.conv2_bn(F.relu(self.conv2(out))), 2)
+        layer_outs['conv2'] = out
         # out = F.relu(self.conv2(out))
         # out = F.dropout(out)
         # out = F.max_pool1d(out, 2)
@@ -486,7 +489,10 @@ class simple_net(torch.nn.Module):
         # out = F.dropout(out)
         # out = F.max_pool1d(out, 2)
         out = out.view(out.size(0), -1)
+        layer_outs['fc_inp'] = out
         out = F.relu(self.lin1(out))
+        layer_outs['fc1'] = out
         # out = F.dropout(out)
         out = self.lin2(out)
-        return out
+        layer_outs['fc2'] = out
+        return out, layer_outs

### 2018-02-06 code/graph_cnn_ecg/nn_trainer.py

@@ -114,7 +114,7 @@ class simple_trainer:
                 # label = Variable(sample['label'])
                 self.optimizer.zero_grad()
                 # pdb.set_trace()
-                y_pred = self.nn_model(instance)
+                y_pred, pred_layer_outs = self.nn_model(instance)
                 y_pred = y_pred.view(-1, 2)
                 # pdb.set_trace()
                 loss = self.loss_fn(y_pred, label)
@@ -151,7 +151,7 @@ class simple_trainer:
         tot_num = 0
         for sample in self.test_loader:
             instance = Variable(sample['sig'].cuda())
-            y_pred = self.nn_model(instance)
+            y_pred, pred_layer_outs = self.nn_model(instance)
             # pdb.set_trace()
             y_pred = y_pred.view(-1, 2)
             _, label_pred = torch.max(y_pred.data, 1)

### 2018-02-20 code/graph_cnn_ecg/ecg_cnn_graph_robust.py
Small commit

@@ -63,7 +63,7 @@ if __name__ == "__main__":
                                       ecg_test_loader, loss_fn)
         simple_train.train_model(50, plt_fig=False)
 
-        # Get all the weights from the CNN
+        # Get all the last layer predn from the CNN
         # Put the weights onto the graph
         # graph structure to learn on is very small
         # Basically equivalent to making N different

### 2018-02-20 code/graph_cnn_ecg/nn_trainer.py
WhatamIdoingwithmylife

@@ -2,6 +2,7 @@ import torch
 from torch.autograd import Variable
 import matplotlib.pyplot as plt
 import numpy as np
+import shutil
 
 if torch.cuda.is_available():
     print('cuda available')
@@ -13,6 +14,12 @@ else:
     dtypeFloat = torch.FloatTensor
     dtypeLong = torch.LongTensor
     torch.manual_seed(1)
+
+
+def save_checkpoint(state, is_best, filename='checkpoint.pth.tar'):
+    torch.save(state, filename)
+    if is_best:
+        shutil.copyfile(filename, 'model_best.pth.tar')
 
 
 class ecg_trainer:
@@ -105,6 +112,8 @@ class simple_trainer:
             ax.set_xlim(0, num_epoch)
             ax.set_ylim(0, 1)
             line, = ax.plot(epoch_list, val_acc, 'ko-')
+        curr_acc = 0
+        best_acc = 0
         for epoch in range(num_epoch):
             running_loss = 0
             num_tr_iter = 0
@@ -139,11 +148,28 @@ class simple_trainer:
 
             # self.valid_acc_list.append(val_acc)
             else:
-                self.test_model()
+                curr_acc = self.test_model()
+                is_best = False
+                if curr_acc > best_acc:
+                    best_acc = curr_acc
+                    is_best = True
+                    save_checkpoint({
+                        'epoch': epoch + 1,
+                        # 'arch': args.arch,
+                        'state_dict': self.nn_model.state_dict(),
+                        # 'best_prec1': best_prec1,
+                        'optimizer': self.optimizer.state_dict(),
+                    }, is_best)
         if plt_fig:
             return fig
         else:
             return
+
+    def get_nn_features(self, instance):
+        # for ind, sample in enumerate(self.train_loader):
+            # instance = Variable(sample['sig'].cuda())
+        y_pred, pred_layer_outs = self.nn_model(instance)
+        return pred_layer_outs['fc1']
 
     def test_model(self):
         print('TestSet :', len(self.test_loader))
@@ -163,3 +189,12 @@ class simple_trainer:
             tot_num += 1
         print(num_corr, tot_num, num_corr/tot_num)
         return num_corr/tot_num
+
+    def graph_nn_train(self, num_epoch=10):
+        for epoch in range(num_epoch):
+            running_loss = 0
+            num_tr_iter = 0
+            for ind, sample in enumerate(self.train_loader):
+                instance = Variable(sample['sig'].cuda())
[…]

### 2018-02-22 code/graph_cnn_ecg/cfg.py
A bit more progress

@@ -3,7 +3,7 @@ def all_vars():
     all_var['Din'] = 750
     all_var['batch_size'] = 4
     all_var['num_tr_points'] = 300
-    all_var['channels'] = [7]
+    all_var['channels'] = [7, 8]
     return all_var
 
 

### 2018-02-22 code/graph_cnn_ecg/data_loader.py

@@ -49,7 +49,7 @@ class ecg_dataset(Dataset):
             out_label = 0
         # pdb.set_trace()
 
-        sample = {'sig': sig_out, 'label': out_label}
+        sample = {'sig': sig_out, 'label': out_label, 'idx': idx, 'pidx': pidx}
         return sample
 
 

### 2018-02-22 code/graph_cnn_ecg/ecg_cnn_graph_robust.py

@@ -4,7 +4,7 @@ from torch.autograd import Variable
 # from torch.utils.data import Dataset, DataLoader
 from torch.utils.data import DataLoader
 from data_loader import ecg_dataset_simple
-from nn_model import simple_net
+from nn_model import simple_net, complex_net
 from nn_trainer import simple_trainer
 import torch.nn.functional as F
 import numpy as np
@@ -57,7 +57,8 @@ if __name__ == "__main__":
                                                         partitions=batch_size, channels=channels),
                                      batch_size=batch_size, shuffle=False, num_workers=2)
 
-        simple_nn = simple_net(Din, len(channels))
+        # simple_nn = simple_net(Din, len(channels))
+        simple_nn = complex_net(Din, len(channels))
         loss_fn = torch.nn.CrossEntropyLoss()
         simple_train = simple_trainer(simple_nn, ecg_train_loader,
                                       ecg_test_loader, loss_fn)

### 2018-02-22 code/graph_cnn_ecg/nn_model.py

@@ -496,3 +496,80 @@ class simple_net(torch.nn.Module):
         out = self.lin2(out)
         layer_outs['fc2'] = out
         return out, layer_outs
+
+
+class complex_net(torch.nn.Module):
+    def __init__(self, D_in, inp_channels):
+        super(complex_net, self).__init__()
+        # For conv1d the params are N, C, L
+        # N is the batch size
+        # C is the number of channels
+        # L is the len of the signal
+        # For now keep the number of channels=1
+        f = 3
+        s = 1
+        self.conv1_list = []
+        # for i in range(inp_channels):
+        # self.conv1_list.append(torch.nn.Conv1d(1, 6, f, stride=s))
+        new_dim = calc_dim(D_in, f, s) // 2
+        self.conv1_bn = torch.nn.BatchNorm1d(6)
+        self.conv2_list = []
+        # for i in range(inp_channels):
+        # self.conv2_list.append(torch.nn.Conv1d(6, 16, f, stride=s))
+        new_dim = calc_dim(new_dim, f, s) // 2
+        self.conv2_bn = torch.nn.BatchNorm1d(16)
+        # self.conv3 = torch.nn.Conv1d(16, 32, f, stride=s)
+        # new_dim = calc_dim(new_dim, f, s) // 2
+        self.lin1_list = []
+        # for i in range(inp_channels):
+        # self.lin1_list.append(torch.nn.Linear(16*new_dim, 30))
+        self.lin2_list = []
+        for i in range(inp_channels):
+            self.conv1_list.append(torch.nn.Conv1d(1, 6, f, stride=s))
+            self.conv2_list.append(torch.nn.Conv1d(6, 16, f, stride=s))
+            self.lin1_list.append(torch.nn.Linear(16*new_dim, 30))
+            self.lin2_list.append(torch.nn.Linear(30, 2))
+
+    def forward(self, inp):
+        # out = F.relu(F.max_pool1d(self.conv1_bn(self.conv1(inp)), 2))
+        num_channels = inp.shape[1]
+        channel_layer_outs = []
+
+        for i in range(num_channels):
+            layer_outs = dict()
+            # pdb.set_trace()
+            # inp_chan = inp[:, ]
+            out = F.max_pool1d(self.conv1_bn(F.relu(self.conv1_list[i](inp[:, [i], :]))), 2)
+            layer_outs['conv1'] = out
[…]

### 2018-02-22 code/graph_cnn_ecg/nn_trainer.py

@@ -3,6 +3,7 @@ from torch.autograd import Variable
 import matplotlib.pyplot as plt
 import numpy as np
 import shutil
+import pickle
 
 if torch.cuda.is_available():
     print('cuda available')
@@ -165,11 +166,11 @@ class simple_trainer:
         else:
             return
 
-    def get_nn_features(self, instance):
-        # for ind, sample in enumerate(self.train_loader):
-            # instance = Variable(sample['sig'].cuda())
-        y_pred, pred_layer_outs = self.nn_model(instance)
-        return pred_layer_outs['fc1']
+    # def get_nn_features(self, instance):
+    #     # for ind, sample in enumerate(self.train_loader):
+    #         # instance = Variable(sample['sig'].cuda())
+    #     y_pred, pred_layer_outs = self.nn_model(instance)
+    #     return pred_layer_outs
 
     def test_model(self):
         print('TestSet :', len(self.test_loader))
@@ -190,11 +191,28 @@ class simple_trainer:
         print(num_corr, tot_num, num_corr/tot_num)
         return num_corr/tot_num
 
-    def graph_nn_train(self, num_epoch=10):
-        for epoch in range(num_epoch):
-            running_loss = 0
-            num_tr_iter = 0
-            for ind, sample in enumerate(self.train_loader):
-                instance = Variable(sample['sig'].cuda())
-                label = Variable(sample['label'].cuda())
-                last_layer_features = self.get_nn_features(instance)
+    def cnn_features_save(self):
+        out_train_list = []
+        for ind, sample in enumerate(self.train_loader):
+            out_train = dict()
+            instance = Variable(sample['sig'].cuda())
+            # label = Variable(sample['label'].cuda())
+            idx = sample['idx']
+            pidx = sample['pidx']
+            y_pred, channel_layer_outs = self.nn_model(instance)
+            out_train['idx'] = idx
+            out_train['pidx'] = pidx
+            out_train['label'] = sample['label']
+            out_train['channel_layer_outs'] = channel_layer_outs
+            out_train_list.append(out_train)
+        pickle.dump(out_train_list, '../data/cnn_features.pkl')
+
+    # def graph_nn_train(self, num_epoch=10):
+    #     for epoch in range(num_epoch):
+    #         running_loss = 0
+    #         num_tr_iter = 0
+    #         for ind, sample in enumerate(self.train_loader):
+    #             instance = Variable(sample['sig'].cuda())
[…]

### 2018-02-23 code/graph_cnn_ecg/ecg_cnn_graph_robust.py
complex net now working

@@ -59,6 +59,8 @@ if __name__ == "__main__":
 
         # simple_nn = simple_net(Din, len(channels))
         simple_nn = complex_net(Din, len(channels))
+        simple_nn.cuda()
+        simple_nn.to_cuda()
         loss_fn = torch.nn.CrossEntropyLoss()
         simple_train = simple_trainer(simple_nn, ecg_train_loader,
                                       ecg_test_loader, loss_fn)

### 2018-02-23 code/graph_cnn_ecg/nn_model.py

@@ -506,6 +506,7 @@ class complex_net(torch.nn.Module):
         # C is the number of channels
         # L is the len of the signal
         # For now keep the number of channels=1
+        self.num_inp_channels = inp_channels
         f = 3
         s = 1
         self.conv1_list = []
@@ -532,9 +533,10 @@ class complex_net(torch.nn.Module):
 
     def forward(self, inp):
         # out = F.relu(F.max_pool1d(self.conv1_bn(self.conv1(inp)), 2))
+        # pdb.set_trace()
         num_channels = inp.shape[1]
         channel_layer_outs = []
-
+        fin_outs = []
         for i in range(num_channels):
             layer_outs = dict()
             # pdb.set_trace()
@@ -549,8 +551,8 @@ class complex_net(torch.nn.Module):
             layer_outs['fc1'] = out
             out = self.lin2_list[i](out)
             layer_outs['fc2'] = out
-            channel_layer_outs[i] = layer_outs
-
+            channel_layer_outs.append(layer_outs)
+            fin_outs.append(out)
         # dict()
 
         # out = F.max_pool1d(self.conv1_bn(F.relu(self.conv1(inp))), 2)
@@ -572,4 +574,13 @@ class complex_net(torch.nn.Module):
         # out = F.dropout(out)
         # out = self.lin2(out)
         # layer_outs['fc2'] = out
+
         return out, channel_layer_outs
+
+    def to_cuda(self):
+        self.cuda()
+        for i in range(self.num_inp_channels):
+            self.conv1_list[i].cuda()
+            self.conv2_list[i].cuda()
+            self.lin1_list[i].cuda()
+            self.lin2_list[i].cuda()

### 2018-02-23 code/graph_cnn_ecg/nn_trainer.py

@@ -92,7 +92,7 @@ class simple_trainer:
     def __init__(self, nn_model, train_loader=None, test_loader=None,
                  loss_fn=None, optimizer='adam'):
         self.nn_model = nn_model
-        self.nn_model.cuda()
+        # self.nn_model.cuda()
         self.train_loader = train_loader
         self.test_loader = test_loader
         self.loss_fn = loss_fn

### 2018-02-23 code/graph_cnn_ecg/cfg.py
Definitely something is amiss, in terms of multiple conv

@@ -3,7 +3,7 @@ def all_vars():
     all_var['Din'] = 750
     all_var['batch_size'] = 4
     all_var['num_tr_points'] = 300
-    all_var['channels'] = [7, 8]
+    all_var['channels'] = [8, 7]
     return all_var
 
 

### 2018-02-23 code/graph_cnn_ecg/ecg_cnn_graph_robust.py

@@ -60,7 +60,7 @@ if __name__ == "__main__":
         # simple_nn = simple_net(Din, len(channels))
         simple_nn = complex_net(Din, len(channels))
         simple_nn.cuda()
-        simple_nn.to_cuda()
+        # simple_nn.to_cuda()
         loss_fn = torch.nn.CrossEntropyLoss()
         simple_train = simple_trainer(simple_nn, ecg_train_loader,
                                       ecg_test_loader, loss_fn)

### 2018-02-23 code/graph_cnn_ecg/nn_model.py

@@ -509,22 +509,22 @@ class complex_net(torch.nn.Module):
         self.num_inp_channels = inp_channels
         f = 3
         s = 1
-        self.conv1_list = []
+        self.conv1_list = torch.nn.ModuleList()
         # for i in range(inp_channels):
         # self.conv1_list.append(torch.nn.Conv1d(1, 6, f, stride=s))
         new_dim = calc_dim(D_in, f, s) // 2
         self.conv1_bn = torch.nn.BatchNorm1d(6)
-        self.conv2_list = []
+        self.conv2_list = torch.nn.ModuleList()
         # for i in range(inp_channels):
         # self.conv2_list.append(torch.nn.Conv1d(6, 16, f, stride=s))
         new_dim = calc_dim(new_dim, f, s) // 2
         self.conv2_bn = torch.nn.BatchNorm1d(16)
         # self.conv3 = torch.nn.Conv1d(16, 32, f, stride=s)
         # new_dim = calc_dim(new_dim, f, s) // 2
-        self.lin1_list = []
+        self.lin1_list = torch.nn.ModuleList()
         # for i in range(inp_channels):
         # self.lin1_list.append(torch.nn.Linear(16*new_dim, 30))
-        self.lin2_list = []
+        self.lin2_list = torch.nn.ModuleList()
         for i in range(inp_channels):
             self.conv1_list.append(torch.nn.Conv1d(1, 6, f, stride=s))
             self.conv2_list.append(torch.nn.Conv1d(6, 16, f, stride=s))
@@ -577,10 +577,85 @@ class complex_net(torch.nn.Module):
 
         return out, channel_layer_outs
 
-    def to_cuda(self):
-        self.cuda()
-        for i in range(self.num_inp_channels):
-            self.conv1_list[i].cuda()
-            self.conv2_list[i].cuda()
-            self.lin1_list[i].cuda()
-            self.lin2_list[i].cuda()
+    # def to_cuda(self):
+    #     self.cuda()
+    #     for i in range(self.num_inp_channels):
+    #         self.conv1_list[i].cuda()
+    #         self.conv2_list[i].cuda()
+    #         self.lin1_list[i].cuda()
+    #         self.lin2_list[i].cuda()
+
+
+# class complex_net2(torch.nn.Module):
+#     def __init__(self, D_in, inp_channels):
+#         super(complex_net2, self).__init__()
+#         # For conv1d the params are N, C, L
[…]

### 2018-02-23 code/graph_cnn_ecg/nn_trainer.py

@@ -207,12 +207,12 @@ class simple_trainer:
             out_train_list.append(out_train)
         pickle.dump(out_train_list, '../data/cnn_features.pkl')
 
-    # def graph_nn_train(self, num_epoch=10):
-    #     for epoch in range(num_epoch):
-    #         running_loss = 0
-    #         num_tr_iter = 0
-    #         for ind, sample in enumerate(self.train_loader):
-    #             instance = Variable(sample['sig'].cuda())
-    #             label = Variable(sample['label'].cuda())
-    #             # last_layer_features = self.get_nn_features(instance)
-    #             y_pred, channel_layer_outs = self.nn_model(instance)
+    def graph_nn_train(self, num_epoch=10):
+        for epoch in range(num_epoch):
+            running_loss = 0
+            num_tr_iter = 0
+            for ind, sample in enumerate(self.train_loader):
+                instance = Variable(sample['sig'].cuda())
+                label = Variable(sample['label'].cuda())
+                # last_layer_features = self.get_nn_features(instance)
+                y_pred, channel_layer_outs = self.nn_model(instance)

### 2018-03-12 code/graph_cnn_ecg/ecg_cnn_graph_robust.py
Finally code is running, now time to wait and watch

@@ -7,8 +7,9 @@ from data_loader import ecg_dataset_simple
 from nn_model import simple_net, complex_net, end_to_end_model
 from nn_model import Graph_ConvNet_LeNet5
 from nn_trainer import simple_trainer, end_to_end_trainer
-import torch.nn.functional as F
-import numpy as np
+# import torch.nn.functional as F
+# import numpy as np
+import pdb
 # import mat
 # import pathlib
 from pathlib import Path
@@ -50,7 +51,10 @@ if __name__ == "__main__":
     test_list = (control_list[contr_tr_pts:] + positive_list[post_tr_pts:] +
                  remainder_list[remain_tr_pts:])
 
-    small_graph = simple_graph()
+    small_graph = simple_graph(n=6, number_edges=5)
+
+    # pdb.set_trace()
+
     coarsening_levels = 2
     L, perm = coarsen(small_graph, coarsening_levels)
 
@@ -74,6 +78,7 @@ if __name__ == "__main__":
     CL2_K = 16
     FC1_F = 30
     FC2_F = 2
+    net_parameters = [D, Fin, CL1_F, CL1_K, CL2_F, CL2_K, FC1_F, FC2_F]
     gnet_parameters = [D, CL1_F, CL1_K, CL2_F, CL2_K, FC1_F, FC2_F]
 
     # Need to define graph_nn
@@ -102,23 +107,23 @@ if __name__ == "__main__":
                                       batch_size=1, shuffle=False, num_workers=0)
 
         # simple_nn = simple_net(Din, len(channels))
-        # simple_nn = complex_net(Din, len(channels))
-        # simple_nn.cuda()
+        simple_nn = complex_net(Din, len(channels))
+        simple_nn.cuda()
         # simple_nn.to_cuda()
-        # graph_nn = Graph_ConvNet_LeNet5(net_parameters)
-        # graph_nn.cuda()
+        graph_nn = Graph_ConvNet_LeNet5(net_parameters)
+        graph_nn.cuda()
         loss_fn = torch.nn.CrossEntropyLoss()
-        # simple_train = simple_trainer(simple_nn, graph_nn, ecg_train_loader, ecg_train_loader2,
-        # ecg_train_loader_graph, ecg_test_loader, ecg_test_loader2,
-        # loss_fn)
-        # simple_train.load_model()
+        simple_train = simple_trainer(simple_nn, graph_nn, ecg_train_loader, ecg_train_loader2,
[…]

### 2018-03-12 code/graph_cnn_ecg/lib/coarsening.py

@@ -372,7 +372,7 @@ def perm_data_torch2(x, indices):
         # They will stay 0 so that max pooling chooses the singelton.
         # Or -infty ?
         else:
-            xnew[i, :, :] = torch.zeros(B, F)
+            xnew[i, :, :] = torch.autograd.Variable(torch.zeros(B, F))
     return xnew
 
 

### 2018-03-12 code/graph_cnn_ecg/lib/grid_graph.py

@@ -7,36 +7,37 @@ import numpy as np
 import pdb
 import itertools
 
-def grid_graph(grid_side,number_edges,metric):
+
+def grid_graph(grid_side, number_edges, metric):
     """Generate graph of a grid"""
     z = grid(grid_side)
     pdb.set_trace()
     dist, idx = distance_sklearn_metrics(z, k=number_edges, metric=metric)
     A = adjacency(dist, idx)
-    print("nb edges: ",A.nnz)
+    print("nb edges: ", A.nnz)
     return A
 
 
 def grid(m, dtype=np.float32):
     """Return coordinates of grid points"""
     M = m**2
-    x = np.linspace(0,1,m, dtype=dtype)
-    y = np.linspace(0,1,m, dtype=dtype)
+    x = np.linspace(0, 1, m, dtype=dtype)
+    y = np.linspace(0, 1, m, dtype=dtype)
     xx, yy = np.meshgrid(x, y)
-    z = np.empty((M,2), dtype)
-    z[:,0] = xx.reshape(M)
-    z[:,1] = yy.reshape(M)
+    z = np.empty((M, 2), dtype)
+    z[:, 0] = xx.reshape(M)
+    z[:, 1] = yy.reshape(M)
     return z
 
 
 def distance_sklearn_metrics(z, k=4, metric='euclidean'):
     """Compute pairwise distances"""
-    #d = sklearn.metrics.pairwise.pairwise_distances(z, metric=metric, n_jobs=-2)
+    # d = sklearn.metrics.pairwise.pairwise_distances(z, metric=metric, n_jobs=-2)
     d = sklearn.metrics.pairwise.pairwise_distances(z, metric=metric, n_jobs=1)
     # k-NN
-    idx = np.argsort(d)[:,1:k+1]
+    idx = np.argsort(d)[:, 1:k+1]
     d.sort()
-    d = d[:,1:k+1]
+    d = d[:, 1:k+1]
     return d, idx
 
 
@@ -48,7 +49,7 @@ def adjacency(dist, idx):
     assert dist.max() <= 1
 
     # Pairwise distances
-    sigma2 = np.mean(dist[:,-1])**2
+    sigma2 = np.mean(dist[:, -1])**2
     dist = np.exp(- dist**2 / sigma2)
 
     # Weight matrix
@@ -85,6 +86,9 @@ def simple_graph(n=6, create_using=None, number_edges=2, metric='euclidean'):
     # return z
     # z[0, 1] =
[…]

### 2018-03-12 code/graph_cnn_ecg/nn_model.py

@@ -441,11 +441,38 @@ class complex_net(torch.nn.Module):
 #             self.lin1_list[i].cuda()
 #             self.lin2_list[i].cuda()
 
+class small_model(torch.nn.Module):
+    def __init__(self, cnet_parameters):
+        super(small_model, self).__init__()
+        Din, num_inp_channels, f, s, c1o, c2o, fc1o = cnet_parameters
+        self.conv1 = torch.nn.Conv1d(1, c1o, f, stride=s)
+        new_dim = calc_dim(Din, f, s) // 2
+        self.conv2 = torch.nn.Conv1d(c1o, c2o, f, stride=s)
+        new_dim = calc_dim(new_dim, f, s) // 2
+        self.lin1 = torch.nn.Linear(c2o*new_dim, fc1o)
+        self.conv1_bn = torch.nn.BatchNorm1d(c1o)
+        self.conv2_bn = torch.nn.BatchNorm1d(c2o)
+
+    def forward(self, inp):
+        out = F.max_pool1d(self.conv1_bn(F.relu(self.conv1(inp))), 2)
+        out = F.max_pool1d(self.conv2_bn(F.relu(self.conv2(out))), 2)
+        out = out.view(out.size(0), -1)
+        out = F.relu(self.lin1(out))
+
+        return out
+
+
 class end_to_end_model(torch.nn.Module):
     def __init__(self, cnet_parameters, gnet_parameters):
         super(end_to_end_model, self).__init__()
         Din, num_inp_channels, f, s, c1o, c2o, fc1o = cnet_parameters
         self.num_inp_channels = num_inp_channels
+        # self.small_model0 = small_model(cnet_parameters)
+        # self.small_model1 = small_model(cnet_parameters)
+        # self.small_model2 = small_model(cnet_parameters)
+        # self.small_model3 = small_model(cnet_parameters)
+        # self.small_model4 = small_model(cnet_parameters)
+        # self.small_model5 = small_model(cnet_parameters)
 
         D, CL1_F, CL1_K, CL2_F, CL2_K, FC1_F, FC2_F = gnet_parameters
         p = 2
@@ -460,13 +487,13 @@ class end_to_end_model(torch.nn.Module):
         self.conv2_bn = torch.nn.BatchNorm1d(c2o)
 
         self.lin1_list = torch.nn.ModuleList()
-        # self.lin2_list = torch.nn.ModuleList()
+        self.lin2_list = torch.nn.ModuleList()
 
[…]

### 2018-03-12 code/graph_cnn_ecg/nn_trainer.py

@@ -385,4 +385,4 @@ class end_to_end_trainer:
             tot_num += 1
         print(num_corr, tot_num, num_corr/tot_num)
         self.nn_model.train()
-        return
+        return num_corr / tot_num

### 2018-03-13 code/graph_cnn_ecg/cfg.py
Partial e2e code written, still need to check performance properly

@@ -3,7 +3,8 @@ def all_vars():
     all_var['Din'] = 750
     all_var['batch_size'] = 4
     all_var['num_tr_points'] = 300
-    all_var['channels'] = [6, 7, 8, 9, 10, 11]
+    # all_var['channels'] = [6, 7, 8, 9, 10, 11]
+    all_var['channels'] = [7]
     return all_var
 
 

### 2018-03-13 code/graph_cnn_ecg/nn_model.py

@@ -495,6 +495,13 @@ class end_to_end_model(torch.nn.Module):
             self.lin1_list.append(torch.nn.Linear(c2o*new_dim, fc1o))
             self.lin2_list.append(torch.nn.Linear(fc1o, 2))
 
+        # self.cnet_module_list = torch.nn.ModuleList([self.conv1_list,
+        #                                              self.conv2_list, self.lin1_list])
+        self.cnet_module_list = torch.nn.ModuleList()
+        for i in range(self.num_inp_channels):
+            tmp_list = torch.nn.ModuleList([self.conv1_list[i], self.conv2_list[i],
+                                            self.lin1_list[i], self.lin2_list[i]])
+            self.cnet_module_list.append(tmp_list)
         # FC1Fin = CL2_F*(D//(p*p))
         # pdb.set_trace()
         # graph CL1
@@ -536,6 +543,9 @@ class end_to_end_model(torch.nn.Module):
         self.fc2.weight.data.uniform_(-scale, scale)
         self.fc2.bias.data.fill_(0.0)
 
+        self.gcnet_module_list = torch.nn.ModuleList([self.cl1, self.cl2, self.fc1, self.fc2])
+        # for p in self.gcnet_module_list.parameters():
+        #     p.requires_grad = False
         # nb of parameters
         nb_param = 18000
         nb_param += CL1_K * CL1_F + CL1_F          # CL1
@@ -622,11 +632,14 @@ class end_to_end_model(torch.nn.Module):
         else:
             return x
 
-    def forward(self, inp, d, L, lmax, perm):
+    def forward(self, inp, d, L, lmax, perm, epoch_num):
+        return self.forward_2(inp, d, L, lmax, perm)
+
+    def forward_2(self, inp, d, L, lmax, perm):
         # pdb.set_trace()
         num_channels = inp.shape[1]
         out_list = []
-
+        pdb.set_trace()
         for i in range(0, num_channels):
             out = F.max_pool1d(self.conv1_bn(F.relu(self.conv1_list[i](inp[:, [i], :]))), 2)
             out = F.max_pool1d(self.conv2_bn(F.relu(self.conv2_list[i](out))), 2)
@@ -699,3 +712,33 @@ class end_to_end_model(torch.nn.Module):
         x = self.fc2(x[:, 0, :])
         # pdb.set_trace()
         return x
+
+
+class partial_end_to_end_model(end_to_end_model):
+    def __init__(self, cnet_parameters, gnet_parameters):
[…]

### 2018-03-13 code/graph_cnn_ecg/nn_trainer.py

@@ -345,7 +345,8 @@ class end_to_end_trainer:
                 label = Variable(sample['label'].type(dtypeLong))
                 # pdb.set_trace()
                 self.optimizer.zero_grad()
-                y_pred = self.nn_model(instance, d, L, lmax, perm)
+                y_pred = self.nn_model(instance, d, L, lmax, perm,
+                                       self.start_epoch + epoch)
                 y_pred = y_pred.view(-1, 2)
                 # pdb.set_trace()
                 loss = self.loss_fn(y_pred, label)
@@ -376,7 +377,7 @@ class end_to_end_trainer:
         self.nn_model.eval()
         for sample in self.test_loader:
             instance = Variable(sample['sig'].cuda())
-            y_pred = self.nn_model(instance, d, L, lmax, perm)
+            y_pred = self.nn_model(instance, d, L, lmax, perm, self.curr_epoch)
             y_pred = y_pred.view(-1, 2)
             _, label_pred = torch.max(y_pred.data, 1)
 

### 2018-03-20 code/graph_cnn_ecg/learn_graph.py
Written code for edge weights as avg signal correlation

@@ -1,0 +1,37 @@
+import networkx as nx
+import numpy as np
+import pdb
+# from torch.utils.data import DataLoader
+from pathlib import Path
+from scipy.stats.stats import pearsonr
+import itertools
+from scipy import sparse
+
+
+class graph_learner:
+    def __init__(self, train_data_loader=None, inp_dim=750, num_nodes=6):
+        self.train_data_loader = train_data_loader
+        self.X = np.zeros((num_nodes, inp_dim))
+        self.adj_mat = np.zeros((num_nodes, num_nodes))
+
+    def get_data(self):
+        for ind, sample in enumerate(self.train_data_loader):
+            instance = sample['sig']
+            tmp = instance.sum(dim=0)
+            self.X += tmp.cpu() / self.train_data_loader.batch_size
+            # pdb.set_trace()
+        self.X = self.X / (ind + 1)
+        return
+
+    def get_graph(self):
+        self.get_data()
+        self.node_vals = self.X.T
+        col_list = np.arange(self.node_vals.shape[1])
+        # pdb.set_trace()
+        for col_a, col_b in itertools.combinations(col_list, 2):
+            val = pearsonr(self.node_vals[:, col_a], self.node_vals[:, col_b])[0]
+            if val > 0:
+                self.adj_mat[col_a, col_b] = val
+                self.adj_mat[col_b, col_a] = val
+        # pdb.set_trace()
+        return sparse.csr_matrix(self.adj_mat)

### 2018-03-21 code/graph_cnn_ecg/ecg_cnn_graph_robust.py
Started bit of documentation (negligible tbh)

@@ -17,6 +17,7 @@ from cfg import all_vars
 from lib.grid_graph import simple_graph
 from lib.coarsening import coarsen
 from lib.coarsening import lmax_L
+from learn_graph import graph_learner
 # from lib.grid_graph import radial_graph
 
 if __name__ == "__main__":
@@ -50,8 +51,14 @@ if __name__ == "__main__":
                   remainder_list[:remain_tr_pts])
     test_list = (control_list[contr_tr_pts:] + positive_list[post_tr_pts:] +
                  remainder_list[remain_tr_pts:])
+    contr_list = (control_list[:contr_tr_pts])
+    ecg_control_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, contr_list,
+                                                       Din, partitions=27, channels=channels),
+                                    batch_size=batch_size, shuffle=True, num_workers=2)
 
-    small_graph = simple_graph(n=6, number_edges=5)
+    new_graph_learner = graph_learner(ecg_control_loader)
+    # small_graph = simple_graph(n=6, number_edges=5)
+    small_graph = new_graph_learner.get_graph()
 
     # pdb.set_trace()
 
@@ -106,8 +113,8 @@ if __name__ == "__main__":
                                                          partitions=27, channels=channels),
                                       batch_size=1, shuffle=False, num_workers=0)
 
-        simple_nn = simple_net(Din, len(channels))
-        # simple_nn = complex_net(Din, len(channels))
+        # simple_nn = simple_net(Din, len(channels))
+        simple_nn = complex_net(Din, len(channels))
         simple_nn.cuda()
         # simple_nn.to_cuda()
         graph_nn = Graph_ConvNet_LeNet5(net_parameters)
@@ -118,7 +125,7 @@ if __name__ == "__main__":
                                       loss_fn)
         # simple_train.load_model()
         simple_train.train_model(50, plt_fig=False)
-        # simple_train.cnn_features_save(fname='/home/SharedData/Ark_git_files/btp_extra_files/ecg-analysis/cnn_features_train.pkl')
+        simple_train.cnn_features_save(fname='/home/SharedData/Ark_git_files/btp_extra_files/cnn_features_train1.pkl')
         # simple_train.graph_nn_train(L, lmax, perm, num_epoch=50)
         # e2e_nn = end_to_end_model(cnet_parameters, gnet_parameters)
         # e2e_trainer = end_to_end_trainer(e2e_nn, ecg_train_loader, ecg_test_loader, loss_fn)

### 2018-03-21 code/graph_cnn_ecg/nn_model.py

@@ -743,7 +743,7 @@ class partial_end_to_end_model(end_to_end_model):
             [self.conv1_complete, self.conv1_bn_complete, self.conv2_complete,
              self.conv2_bn_complete, self.lin1_complete, self.lin2_complete])
         # self.simple_nn_model = simple_net(self.Din, self.num_inp_channels)
-        self.epoch_thresh = 30
+        self.epoch_thresh = 50
 
     def forward_1(self, inp):
         # out = F.max_pool1d(self.conv1_bn(F.relu(self.conv1_list[1](inp[:, [1], :]))), 2)
@@ -777,3 +777,8 @@ class partial_end_to_end_model(end_to_end_model):
             return self.forward_2(inp, d, L, lmax, perm)
         else:
             return self.forward_2(inp, d, L, lmax, perm)
+
+
+class end_to_end_fc_model(partial_end_to_end_model):
+    def __init__(self, cnet_parameters, gnet_parameters):
+        super(end_to_end_fc_model, self).__init__(cnet_parameters, gnet_parameters)

### 2018-03-21 code/graph_cnn_ecg/nn_trainer.py

@@ -8,6 +8,7 @@ import json
 import os
 import pdb
 from lib.coarsening import perm_data_torch2
+import visdom
 
 
 if torch.cuda.is_available():
@@ -213,7 +214,7 @@ class simple_trainer:
         print('TestSet :', len(self.test_loader))
         num_corr = 0
         tot_num = 0
-        self.nn_model.eval()
+        # self.nn_model.eval()
         for sample in self.test_loader:
             instance = Variable(sample['sig'].cuda())
             y_pred, pred_layer_outs = self.nn_model(instance)
@@ -227,7 +228,7 @@ class simple_trainer:
             # tot_num += label_pred.shape[0]
             tot_num += 1
         print(num_corr, tot_num, num_corr/tot_num)
-        self.nn_model.train()
+        # self.nn_model.train()
         return num_corr/tot_num
 
     def cnn_features_save(self, fname='../data/cnn_features.pkl'):
@@ -314,6 +315,12 @@ class end_to_end_trainer:
         self.start_epoch = 0
         if optimizer == 'adam':
             self.optimizer = torch.optim.Adam(self.nn_model.parameters())
+        self.tovis = True
+        if self.tovis:
+            self.vis = visdom.Visdom()
+            self.loss_window = self.vis.line(X=torch.zeros((1)).cpu(), Y=torch.zeros((1)).cpu(),
+                                             opts=dict(xlabel='minibatches', ylabel='Loss',
+                                                       title='Training Loss', legend=['Loss']))
 
     def save_checkpoint1(state, is_best, filename='checkpoint_e2e.pth.tar'):
         # f = open(filename, 'w')
@@ -338,6 +345,7 @@ class end_to_end_trainer:
 
     def train_model(self, d, L, lmax, perm, num_epoch=15):
         print('TrainSet: ', len(self.train_loader))
+        self.tot_ind = len(self.train_loader)
         self.nn_model.train()
         curr_acc = 0
         best_acc = 0
@@ -358,6 +366,16 @@ class end_to_end_trainer:
                 self.optimizer.step()
                 running_loss += loss.data[0]
                 num_tr_iter += 1
+
+                if self.tovis:
+                    # pdb.set_trace()
+                    self.vis.line(
+                        X=torch.ones((1)).cpu() * (ind + (self.start_epoch + epoch)
+                                                   * self.tot_ind),
+                        Y=torch.Tensor([loss.data[0]]).cpu(),
+                        win=self.loss_window,
[…]

### 2018-03-22 code/graph_cnn_ecg/ecg_cnn_graph_robust2.py
Added only fc layers code, but there seems to be some problem

@@ -5,6 +5,7 @@ from torch.autograd import Variable
 from torch.utils.data import DataLoader
 from data_loader import ecg_dataset_simple
 from nn_model import simple_net, complex_net, end_to_end_model
+from nn_model import partial_end_to_end_model, end_to_end_fc_model
 from nn_model import Graph_ConvNet_LeNet5
 from nn_trainer import simple_trainer, end_to_end_trainer
 # import torch.nn.functional as F
@@ -17,8 +18,9 @@ from cfg import all_vars
 from lib.grid_graph import simple_graph
 from lib.coarsening import coarsen
 from lib.coarsening import lmax_L
-from learn_graph import graph_learner
 # from lib.grid_graph import radial_graph
+from learn_graph import graph_learner
+
 
 if __name__ == "__main__":
     ptb_tdir = Path('/home/SharedData/Ark_git_files/btp_extra_files/ecg-analysis/')
@@ -52,18 +54,19 @@ if __name__ == "__main__":
     test_list = (control_list[contr_tr_pts:] + positive_list[post_tr_pts:] +
                  remainder_list[remain_tr_pts:])
     contr_list = (control_list[:contr_tr_pts])
+    # small_graph = simple_graph(n=6, number_edges=5)
+
+    # pdb.set_trace()
+
     ecg_control_loader = DataLoader(ecg_dataset_simple(ptb_tdir_str, contr_list,
                                                        Din, partitions=27, channels=channels),
                                     batch_size=batch_size, shuffle=True, num_workers=2)
 
     new_graph_learner = graph_learner(ecg_control_loader)
-    # small_graph = simple_graph(n=6, number_edges=5)
-    small_graph = new_graph_learner.get_graph()
-
-    # pdb.set_trace()
+    new_graph = new_graph_learner.get_graph()
 
     coarsening_levels = 2
-    L, perm = coarsen(small_graph, coarsening_levels)
+    L, perm = coarsen(new_graph, coarsening_levels)
 
     lmax = []
     for i in range(coarsening_levels):
@@ -89,7 +92,7 @@ if __name__ == "__main__":
     gnet_parameters = [D, CL1_F, CL1_K, CL2_F, CL2_K, FC1_F, FC2_F]
 
     # Need to define graph_nn
-    d = 0.5                     # dropout value
+    d = 0                     # dropout value
     with torch.cuda.device(1):
[…]

### 2018-03-22 code/graph_cnn_ecg/nn_model.py

@@ -782,3 +782,55 @@ class partial_end_to_end_model(end_to_end_model):
 class end_to_end_fc_model(partial_end_to_end_model):
     def __init__(self, cnet_parameters, gnet_parameters):
         super(end_to_end_fc_model, self).__init__(cnet_parameters, gnet_parameters)
+        self.gfn = torch.nn.Linear(30 * 6, 30)
+        self.gfn2 = torch.nn.Linear(30, 2)
+
+    def forward_3(self, inp):
+        num_channels = inp.shape[1]
+        out_list = []
+        # pdb.set_trace()
+        for i in range(0, num_channels):
+            out = F.max_pool1d(self.conv1_bn_list[i](
+                F.relu(self.conv1_list[i](inp[:, [i], :]))), 2)
+            out = F.max_pool1d(self.conv2_bn_list[i](F.relu(self.conv2_list[i](out))), 2)
+            out = out.view(out.size(0), -1)
+            # out = out.detach()
+            out = F.relu(self.lin1_list[i](out))
+            # out1 = self.lin2_list[i](out)
+            # cout_var = torch.cat((cout_var, out), 0)
+            out_list.append(out)
+
+        b, f = out.shape        #
+        # out_list = [out0, out1, out2, out3, out4, out5]
+        cout_var = torch.cat(out_list, 0)
+        # cout_var = cout_var.detach()
+        cout_var = cout_var.view(num_channels, b, f)
+        cout_var = cout_var.permute(1, 0, 2)
+        cout_var = cout_var.view(b, num_channels * f)
+        out1 = self.gfn(cout_var)
+        out2 = self.gfn2(out1)
+
+        return out2
+
+    # def forward(self, inp, epoch_num):
+    def forward(self, inp, d, L, lmax, perm, epoch_num):
+        # cnn_trained_bool = False
+        if epoch_num < self.epoch_thresh:
+            return self.forward_1(inp)
+        elif epoch_num == self.epoch_thresh:
+            # l1 = [0, 2, 3, 4, 5]
+            pretrained_dict = self.cnet_complete_module_list.state_dict()
+            # pdb.set_trace()
+            for i, m in enumerate(self.cnet_module_list):
+                # model_dict = m.state_dict()
+                pret_dict = {k: v for k, v in pretrained_dict.items()}
+                for k, v in pretrained_dict.items():
+                    if k == '0.weight':
+                        # pdb.set_trace()
+                        pret_dict[k] = v[:, [i], :]
[…]

### 2018-03-22 code/graph_cnn_ecg/nn_trainer.py

@@ -231,10 +231,14 @@ class simple_trainer:
         # self.nn_model.train()
         return num_corr/tot_num
 
-    def cnn_features_save(self, fname='../data/cnn_features.pkl'):
+    def cnn_features_save(self, train_bool=False, fname='../data/cnn_features.pkl'):
         out_train_list = dict()
         sample_count = 0
-        for ind, sample in enumerate(self.train_loader2):
+        loader = self.test_loader2
+        if train_bool:
+            loader = self.train_loader2
+
+        for ind, sample in enumerate(loader):
             # for ind, sample in enumerate(self.test_loader2):
             out_train = dict()
             instance = Variable(sample['sig'].cuda())

### 2018-03-24 code/graph_cnn_ecg/ecg_cnn_graph_robust.py
Prev error was due to visdom server not being opened and multiproc

@@ -125,8 +125,8 @@ if __name__ == "__main__":
                                       loss_fn)
         # simple_train.load_model()
         simple_train.train_model(50, plt_fig=False)
-        simple_train.cnn_features_save(train_bool=True, fname='/home/SharedData/Ark_git_files/btp_extra_files/cnn_features_train1.pkl')
-        simple_train.cnn_features_save(train_bool=False, fname='/home/SharedData/Ark_git_files/btp_extra_files/cnn_features_test1.pkl')
+        # simple_train.cnn_features_save(train_bool=True, fname='/home/SharedData/Ark_git_files/btp_extra_files/cnn_features_train1.pkl')
+        # simple_train.cnn_features_save(train_bool=False, fname='/home/SharedData/Ark_git_files/btp_extra_files/cnn_features_test1.pkl')
         # simple_train.graph_nn_train(L, lmax, perm, num_epoch=50)
         # e2e_nn = end_to_end_model(cnet_parameters, gnet_parameters)
         # e2e_trainer = end_to_end_trainer(e2e_nn, ecg_train_loader, ecg_test_loader, loss_fn)

### 2018-03-24 code/graph_cnn_ecg/ecg_cnn_graph_robust2.py

@@ -133,8 +133,8 @@ if __name__ == "__main__":
         # e2e_nn = end_to_end_model(cnet_parameters, gnet_parameters)
         # e2e_nn = partial_end_to_end_model(cnet_parameters, gnet_parameters)
         e2e_nn = end_to_end_fc_model(cnet_parameters, gnet_parameters)
-        e2e_trainer = end_to_end_trainer(e2e_nn, ecg_train_loader, ecg_test_loader, loss_fn)
-        e2e_trainer.load_model()
+        e2e_trainer = end_to_end_trainer(e2e_nn, ecg_train_loader, ecg_test_loader, loss_fn, tovis=False)
+        # e2e_trainer.load_model()
         e2e_trainer.train_model(d, L, lmax, perm, num_epoch=100)
         # get all the last layer predn from the CNN
         # Put the weights onto the graph

### 2018-03-24 code/graph_cnn_ecg/nn_model.py

@@ -806,6 +806,7 @@ class end_to_end_fc_model(partial_end_to_end_model):
         # cout_var = cout_var.detach()
         cout_var = cout_var.view(num_channels, b, f)
         cout_var = cout_var.permute(1, 0, 2)
+        cout_var = cout_var.contiguous()
         cout_var = cout_var.view(b, num_channels * f)
         out1 = self.gfn(cout_var)
         out2 = self.gfn2(out1)

### 2018-03-24 code/graph_cnn_ecg/nn_trainer.py

@@ -309,7 +309,7 @@ class simple_trainer:
 
 class end_to_end_trainer:
     def __init__(self, nn_model, train_loader=None, test_loader=None,
-                 loss_fn=None, optimizer='adam'):
+                 loss_fn=None, optimizer='adam', tovis=False):
         self.nn_model = nn_model
         if torch.cuda.is_available():
             self.nn_model.cuda()
@@ -319,7 +319,7 @@ class end_to_end_trainer:
         self.start_epoch = 0
         if optimizer == 'adam':
             self.optimizer = torch.optim.Adam(self.nn_model.parameters())
-        self.tovis = True
+        self.tovis = tovis
         if self.tovis:
             self.vis = visdom.Visdom()
             self.loss_window = self.vis.line(X=torch.zeros((1)).cpu(), Y=torch.zeros((1)).cpu(),

### 2018-03-24 code/graph_cnn_ecg/small_test_for_error.py

@@ -1,0 +1,52 @@
+import torch
+from torch.autograd import Variable
+import pdb
+import visdom
+import logging
+
+
+def loggerConfig(log_file, verbose=2):
+    logger = logging.getLogger()
+    formatter = logging.Formatter('[%(levelname)-8s] (%(processName)-11s) %(message)s')
+    fileHandler = logging.FileHandler(log_file, 'w')
+    fileHandler.setFormatter(formatter)
+    logger.addHandler(fileHandler)
+    if verbose >= 2:
+        logger.setLevel(logging.DEBUG)
+    elif verbose >= 1:
+        logger.setLevel(logging.INFO)
+    else:
+        # NOTE: we currently use this level to log to get rid of visdom's info printouts
+        logger.setLevel(logging.WARNING)
+    return logger
+
+
+if __name__ == '__main__':
+    # loss_fn = torch.nn.CrossEntropyLoss()
+    # a1 = []
+    # for i in range(5):
+    #     a1.append(Variable(torch.rand(1, 5)))
+    # lin_list = torch.nn.ModuleList()
+    # for i in range(5):
+    #     lin_list.append(torch.nn.Linear(5, 2))
+
+    # a2 = []
+    # for i in range(5):
+    #     a2.append(lin_list[i](a1[i]))
+    # lab = torch.LongTensor([1])
+    # for i in range(5):
+    #     y_pred = a2[i]
+    #     label = Variable(lab)
+    #     yp = y_pred.view(-1, 2)
+    #     # pdb.set_trace()
+    #     loss = loss_fn(yp, label)
+    #     loss.backward()
+    log_name = './logs/'
+    logger = loggerConfig(log_name, 2)
+    logger.warning("<====================>")
+
+    vis = visdom.Visdom()
+    logger.warning("bash$: python -m visdom.server")
+    logger.warning("http://localhost:8097/env/")
+    # while 1:
+    #     pass

### 2018-03-24 code/graph_cnn_ecg/data_loader.py
Written code in data loader for preproc

@@ -54,14 +54,21 @@ class ecg_dataset(Dataset):
 
 
 class ecg_dataset_simple(Dataset):
-    def __init__(self, tdir, patient_list, din, partitions=1, channels=[7]):
+    def __init__(self, tdir, patient_list, din, partitions=1, channels=[7],
+                 topreproc=False, preproc_params=None):
         self.tdir = tdir
         self.patient_list = patient_list
         self.batch_sig_len = din
         self.partitions = partitions
         self.channels = channels
+        self.topreproc = topreproc
+        self.preproc_mu = preproc_params[0]
+        self.preproc_sig = preproc_params[1]
         # self.batch_sig_len = batch_sig_len
         # self.disease
+
+    def preproc(self, dat):
+        return (dat - self.preproc_mu) / self.preproc_sig
 
     def __len__(self):
         return len(self.patient_list)*self.partitions
@@ -79,6 +86,8 @@ class ecg_dataset_simple(Dataset):
         sig, fields = wfdb.srdsamp(self.tdir + self.patient_list[idx], channels=self.channels,
                                    sampfrom=st_pt, sampto=end_pt)
         sig_out = sig.T.astype(np.float32)
+        if self.topreproc:
+            sig_out = self.preproc(sig_out)
         # if has mycardial infraction give out label 1, else 0
         # temporary setting, may use seq2seq at a later time
         # if 'Myocardial Infarction'fields['comments'][4]:
